### 2024-05-24 paper/paper.tex
generate paper after setting up build environment

% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

\begin{document}

\input{header}

\maketitle

\begin{abstract}

Blank localization (also known as workpiece referencing) is an essential task when machining parts.
In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely defined/searched. We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a mostly automated way.
The heart of the procedure is a convex quadratically constrained quadratic program (QCQP).
To easily access the solver, the BlankLocalizationCore.jl package was developed.
Its flexibility and extensibility make it an excellent research tool, that can be deployed in production as well.

\end{abstract}

\section{Introduction}

The \LaTeX{} document preparation system is a special version of the
\TeX; typesetting program where-in a collection of \TeX; commands
are added to \LaTeX{} to simplify typesetting. Importantly, it allows
the author to concentrate on the logical structure of the document
rather than its visual layout.\vskip 6pt
Moreover, \LaTeX{} provides a consistent and comprehensive document
preparation interface. There are simple-to-use commands for
generating a table of contents, lists of figures and/or tables, and indexes.
\LaTeX{} can automatically number list entries, equations, figures,
tables, and footnotes, as well as articles, sections, and subsections.
Using this numbering system, bibliographic citations, page
references, and cross references to any other numbered entity (e.g.
article, section, equation, figure, list entry, etc.) become quite simple
and straightforward. The use of \LaTeX{} document classes allows
a simple change of class to transform the appearance of your document.\vskip 6pt
\LaTeX{} is a powerful tool for managing long and complex documents.
In particular, partial processing enables long documents to
be produced article by article without losing sequential information.
The use of document classes allows a simple change of style
(or style option) to transform the appearance of your document.

\section{The JuliaCon Article Class}
\label{sec:documentclass}
%
The juliacon class file preserves the standard LATEX{} interface such
that any document that can be produced using the standard LATEX{}
article class can also be produced with the class file.\vskip 6pt
It is likely that the make up will change after file submission. For
this reason, we ask you to ignore details such as slightly long lines,
page stretching, or figures falling out of synchronization, as these
details can be dealt with at a later stage.\vskip 6pt
Use should be made of symbolic references (\verb|\ref| ) in order to
protect against late changes of order, etc.

\section{USING THE JuliaCon Article CLASS FILE}

If the file \verb|juliacon.cls|  is not already in the appropriate system directory
for \LaTeX{} files, either arrange for it to be put there or copy
it to your working directory. The \verb|juliacon|  document class is implemented
as a complete class, not a document style option. In order to
use the \verb|juliacon  document class, replace \verb|article|  by \verb|juliacon|  in the
\verb|\documentclass|  command at the beginning of your document:
\vskip 6pt
\begin{centering}
    \verb|\documentclass{article}|  \end{centering}
\vskip 6pt
replace by
\vskip 6pt
 \verb|\documentclass{juliacon}|  \vskip 6pt
In general, the following standard document \verb|style|  options should
{ \itshape not} be used with the {\footnotesize \itshape article} class file:
\begin{enumerate}
\item[(1)] \verb|10pt|,  \verb|11pt|,  \verb|12pt|   ? unavailable;
\item[(2)] \verb|twoside|  (no associated style file) ? \verb|twoside|  is the default;
\item[(3)] \verb|fleqn|, \verb|leqno|, \verb|titlepage| ? should not be used;
\end{enumerate}

\section{Additional Document Style Options}
\label{sec:additional_doc}
%
The following additional style option is available with the \verb|juliacon|  class file:
\vskip 6pt
Please place any additional command definitions at the very start of
the \LaTeX{} file, before the \verb|\begin{document}|. For example, user-defined
\verb|\def|  and \verb|\newcommand|   commands that define macros for
technical expressions should be placed here. Other author-defined
macros should be kept to a minimum.
\vskip 6pt
Commands that differ from the standard \LaTeX{} interface, or that
are provided in addition to the standard interface, are explained in
this guide. This guide is not a substitute for the \LaTeX{} manual itself.
Authors planning to submit their papers in \LaTeX{} are advised to use
\verb|juliacon.cls|  as early as possible in the creation of their files.

%
%
%
%
\begin{table*}[t]
\tabcolsep22pt
\tbl{If necessary, the tables can be extended both columns.}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\label{tab:symbols}
\begin{tabnote}
This is an example of table footnote.
\end{tabnote}
\end{table*}
% \begin{figure*}[t]
% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
% \caption{If necessary, the images can be extended both columns.}
%   \label{fig:sample_image}
% \end{figure*}

\section{Additional features}
\label{sec:additional_faci}
In addition to all the standard \LaTeX{} design elements, the \verb|juliacon|  class file includes the following features:
In general, once you have used the additional \verb|juliacon.cls| facilities
in your document, do not process it with a standard \LaTeX{} class
file.

\subsection{Titles, Author's Name, and Affiliation}
\label{subsub:title_auth}
The title of the article, author's name, and affiliation are used at the
beginning of the article (for the main title). These can be produced
using the following code:

\begin{verbatim}
\title{ This is an example of article title} }
\author{
   \large 1st Author \\[-3pt]
   \normalsize 1st author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	1st author's email address \\[-3pt]
  \and
   \large 2nd Author \\[-3pt]
   \normalsize 2nd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	2nd author's email address \\[-3pt]
\and
   \large 3rd Author \\[-3pt]
   \normalsize 3rd author's affiliation  \\[-3pt]
    \normalsize 1st line of address \\[-3pt]
    \normalsize 2nd line of address \\[-3pt]
    \normalsize	3rd author's email address \\[-3pt]
}
\maketitle
\end{verbatim}

\subsection{Writing Julia code}

A special environment is already defined for Julia code,
built on top of \textit{listings} and \textit{jlcode}.

\begin{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[
    language = Julia, 
    numbers=left, 
    label={lst:exmplg}, 
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}

\subsection{Abstracts, Key words, term etc...}
\label{subsub:abs_key_etc}

At the beginning of your article, the title should be generated
in the usual way using the \verb|\maketitle|  command. For genaral tem and keywords use
\verb|\terms|,
\verb|\keywords|  commands respectively. The abstract should be enclosed
within an abstract environment, All these environment
can be produced using the following code:
\begin{verbatim}
\terms{Experimentation, Human Factors}

\keywords{Face animation, image-based modelling...}

\begin{abstract}
In this paper, we propose a new method for the
systematic determination of the model's base of
time varying delay system. This method based on
the construction of the classification data related
to the considered system. The number, the orders,
the time delay and the parameters of the local
models are generated automatically without any
knowledge about the full operating range of the
process. The parametric identification of the local
models is realized by a new recursive algorithm for
on line identification of systems with unknown time
delay. The proposed algorithm allows simultaneous
estimation of time delay and parameters of
discrete-time systems. The effectiveness of
the new method has been illustrated through
simulation.
\end{abstract}

\end{verbatim}

\section{Some guidelines}
\label{sec:some_guide}
The following notes may help you achieve the best effects with the
\verb|juliacon|  class file.

\subsection{Sections}
\label{subsub:sections}
\LaTeXe{}  provides four levels of section headings and they are all
defined in the \verb|juliacon|  class file:
\begin{itemize}
\item \verb|\section|
\item \verb|\subsection|
\item \verb|\subsubsection|
\item \verb|\paragraph|
\end{itemize}
Section headings are automatically converted to allcaps style.
\subsection{Lists}
\label{sec:lists}
%
The \verb|juliacon|   class file provides unnumbered lists using the
\verb|unnumlist|  environment for example,

\begin{unnumlist}
\item First unnumbered item which has no label and is indented from the
left margin.
\item Second unnumbered item.
\item Third unnumbered item.
\end{unnumlist}
The unnumbered list which has no label and is indented from the
left margin. was produced by:
\begin{verbatim}
\begin{unnumlist}
\item First unnumbered item...
\item Second unnumbered item...
\item Third unnumbered item...
\end{unnumlist}
\end{verbatim}

The \verb|juliacon|  class file also provides hyphen list using the
\verb|itemize|  environment for example,
\begin{itemize}
\item First unnumbered bulleted item which has no label and is indented
from the left margin.
\item Second unnumbered bulleted item.
\item Third unnumbered bulleted item which has no label and is indented
from the left margin.
\end{itemize}
was produced by:
\begin{verbatim}
\begin{itemize}
\item First item...
\item Second item...
\item Third item...
\end{itemize}
\end{verbatim}

Numbered list is also provided in acmtog class file using the
enumerate environment for example,
\begin{enumerate}
\item The attenuated and diluted stellar radiation.
\item Scattered radiation, and
\item Reradiation from other grains.
\end{enumerate}

was produced by:
\begin{verbatim}
\begin{enumerate}
\item The attenuated...
\item Scattered radiation, and...
\item Reradiation from other grains...
\end{enumerate}
\end{verbatim}
\subsection{Illustrations (or figures)}
\label{subsub:sec_Illus}
The \verb|juliacon|  class file will cope with most of the positioning of
your illustrations and you should not normally use the optional positional
qualifiers on the \verb|figure|  environment that would override
these decisions.
\vskip 6pt

%
\begin{figure}[t]
\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
\caption{This is example of the image in a column.}
	\label{fig:sample_figure}
\end{figure}

The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
organization \footnote{https://github.com/JuliaGraphs}.

Figure captions should be \emph{below} the figure itself, therefore the
\verb|\caption|  command should appear after the figure or space left for
an illustration. For example, Figure 1 is produced using the following
commands:

\begin{verbatim}
\begin{figure}
\centerline{\includegraphics[width=20pc]{Graphics.eps}}
\caption{An example of the testing process for a
binary tree. The globa null hypothesis is tested
first at level $\alpha$ (a), and the level of
individual variables is reached last (d). Note
that individual hypotheses can be tested at
level $\alpha/4$ and not $\alpha/8$ as one might
expect at first.}
\label{sample-figure_2}
\end{figure}
\end{verbatim}
Figures can be resized using first and second argument of
\verb|\includegraphics|   command. First argument is used for modifying
figure height and the second argument is used for modifying
figure width respectively.
\vskip 6pt
Cross-referencing of figures, tables, and numbered, displayed
equations using the \verb|\label|  and \verb|\ref|   commands is encouraged.
For example, in referencing Figure 1 above, we used
\verb|Figure~\ref{sample-figure}|

 \subsection{Tables}
\label{subsub:sec_Tab}
The \verb|juliacon|   class file will cope with most of the positioning of
your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
decisions. Table captions should be at the top.
\begin{verbatim}
\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Train70 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test70 & Testing Data I & & 105\\\hline
Test30 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\end{verbatim}

\begin{table}
\tbl{Tuning Set and Testing Set}{
\begin{tabular}{|l|l|c|c|}\hline
Label & \multicolumn{1}{c|}{Description}
& Number of Users &
Number of Queries\\\hline
Test 1 & Training Data &
\smash{\raise-7pt\hbox{70}} & 104\\
\cline{1-2}\cline{4-4}
Test 2 & Testing Data I & & 105\\\hline
Test 3 & Testing Data II & 30 & 119\\\hline
& Total & 100 & 328\\\hline
\end{tabular}}
\end{table}
\subsection{Landscaping Pages}
\label{subsub:landscaping_pages}
If a table is too wide to fit the standard measure, it may be turned,
with its caption, to 90 degrees. Landscape tables cannot be produced
directly using the \verb|juliacon|   class file because \TeX{} itself cannot
turn the page, and not all device drivers provide such a facility.
The following procedure can be used to produce such pages.
\vskip 6pt
Use the package \verb|rotating|   in your document and change the coding
from
\begin{verbatim}
\begin{table}...\end{table}
to
\begin{sidewaystable}...\end{sidewaystable}
and for figures
\begin{figure}...\end{figure}
to
\begin{sidewaysfigure}...\end{sidewaysfigure}
\end{verbatim}

environments in your document to turn your table on the appropriate
page of your document. For instance, the following code prints
a page with the running head, a message half way down and the
table number towards the bottom.
\begin{verbatim}
\begin{sidewaystable}
\tbl{Landscape table caption to go here.}{...}
\label{landtab}
\end{sidewaystable}
\end{verbatim}

\subsection{Double Column Figure and Tables}
\label{subsub:double_fig_tab}
For generating the output of figures and tables in double column
we can use the following coding:

\begin{enumerate}
\item For Figures:
\begin{verbatim}
\begin{figure*}...\end{figure*}
\end{verbatim}
\item For landscape figures:
\begin{verbatim}
\begin{sidewaysfigure*}...\end{sidewaysfigure*}
\end{verbatim}
\item For Tables:
\begin{verbatim}
\begin{table*}...\end{table*}
\end{verbatim}
\item For landscape tables:
\begin{verbatim}
\begin{sidewaystable*}...\end{sidewaystable*}
\end{verbatim}
\end{enumerate}

\subsection{Typesetting Mathematics}
\label{subsub:type_math}
The \verb|juliacon| class file will set displayed mathematics with center to
the column width, provided that you use the \LaTeXe{} standard of
open and closed square brackets as delimiters.
The equation
\[
\sum_{i=1}^p \lambda_i = (S)
\]

was typeset using the acmtog class file with the commands

\begin{verbatim}
\[
\sum_{i=1}^p \lambda_i = (S)
\]
\end{verbatim}

For display equations, cross-referencing is encouraged. For example,
\begin{verbatim}
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.
\end{verbatim}
The following output is generated with the above coding:
\begin{equation}
(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
\label{eq:samplevar}
\end{equation}
Equation~(\ref{eq:samplevar}) gives the formula for
sample variance.

\subsection{Enunciations}
\label{subsub:enunciation}
The \verb|juliacon|   class file generates the enunciations with the help of
the following commands:
\begin{verbatim}
\begin{theorem}...\end{theorem}
\begin{strategy}...\end{strategy}
\begin{property}...\end{property}
\begin{proposition}...\end{proposition}
\begin{lemma}...\end{lemma}
\begin{example}...\end{example}
\begin{proof}...\end{proof}
\begin{definition}...\end{definition}
\begin{algorithm}...\end{algorithm}
\begin{remark}...\end{remark}
\end{verbatim}
The above-mentioned coding can also include optional arguments
such as
\begin{verbatim}
\begin{theorem}[...]. Example for theorem:
\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven ... created equal.
\end{theorem}
\end{verbatim}

\begin{theorem}[Generalized Poincare Conjecture]
Four score and seven years ago our fathers brought forth,
upon this continent, a new nation, conceived in Liberty,
 and dedicated to the proposition that all men are
created equal.
\end{theorem}

\subsection{Extract}
\label{subsub:extract}
Extract environment should be coded within
\begin{verbatim}
\begin{extract}..\end{extract}
\end{verbatim}

\subsection{Balancing column at last page}
\label{subsub:Balance}
For balancing the both column length at last page use :
\begin{verbatim}
\vadjust{\vfill\pagebreak}
\end{verbatim}

%\vadjust{\vfill\pagebreak}

at appropriate place in your \TeX{} file or in bibliography file.

\section{Handling references}
\label{subsub:references}
References are most easily (and correctly) generated using the
BIBTEX, which is easily invoked via
\begin{verbatim}
\bibliographystyle{juliacon}
\bibliography{ref}
\end{verbatim}
When submitting the document source (.tex) file to external
parties, the ref.bib file should be sent with it.
\cite{bezanson2017julia}

\input{bib.tex}

\end{document}

% Inspired by the International Journal of Computer Applications template

### 2024-05-24 paper/header.tex
generate paper after setting up build environment

% **************GENERATED FILE, DO NOT EDIT**************

\title{BlankLocalizationCore.jl: implementing blank localization in Julia}

\author[1, 2]{Tamás Cserteg}
\author[1]{András Kovács}
\author[1, 3]{József Váncza}
\affil[1]{EPIC Centre of Excellence, HUN-REN Institute for Computer Science and Control (SZTAKI), Budapest H-1111, Hungary}
\affil[2]{Doctoral School of Informatics, ELTE Eötvös Loránd University, Budapest H-1117, Hungary}
\affil[3]{Department of Manufacturing Science and Technology, Budapest University of Technology and Economics, Budapest H-1111, Hungary}

\keywords{Julia, Optimization, Machining, Blank localization}

\hypersetup{
pdftitle = {BlankLocalizationCore.jl: implementing blank localization in Julia},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Tamás Cserteg, András Kovács, József Váncza},
pdfkeywords = {Julia, Optimization, Machining, Blank localization},
}

### 2024-05-24 paper/header.tex
shorten affiliations

@@
 \author[1, 3]{József Váncza}
-\affil[1]{EPIC Centre of Excellence, HUN-REN Institute for Computer Science and Control (SZTAKI), Budapest H-1111, Hungary}
-\affil[2]{Doctoral School of Informatics, ELTE Eötvös Loránd University, Budapest H-1117, Hungary}
-\affil[3]{Department of Manufacturing Science and Technology, Budapest University of Technology and Economics, Budapest H-1111, Hungary}
+\affil[1]{HUN-REN Institute for Computer Science and Control (SZTAKI), Budapest, Hungary}
+\affil[2]{Doctoral School of Informatics, ELTE Eötvös Loránd University, Budapest, Hungary}
+\affil[3]{Department of Manufacturing Science and Technology, Budapest University of Technology and Economics, Budapest, Hungary}
 

### 2024-05-24 paper/paper.tex
start writing

@@
 
-Blank localization (also known as workpiece referencing) is an essential task when machining parts.
+Blank localization (also known as workpiece referencing) is an essential task in machining.
 In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely defined/searched.
-We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a mostly automated way.
-The heart of the procedure is a convex quadratically constrained quadratic program (QCQP).
-To easily access the solver, the BlankLocalizationCore.jl package was developed.
-Its flexibility and extensibility make it an excellent research tool, that can be deployed in production as well.
+We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a semi-automated way.
+It processes measurement of the rough geometry and the machining CNC code to solve a convex quadratically constrained quadratic program (QCQP).
+It gives an optimal solution for given machining allowance - tolerance error, providing a tool for the machinist to find the appropriate balance between the two.
+The flexibility and extensibility of the Julia language helped the development of this algorithm, materializing in the \pkg{BlankLocalizationCore} package.
+Its flexibility and ease of use make it an excellent research tool, that can be deployed in production as well.
 
@@
 
-The \LaTeX{} document preparation system is a special version of the
-\TeX; typesetting program where-in a collection of \TeX; commands
-are added to \LaTeX{} to simplify typesetting. Importantly, it allows
-the author to concentrate on the logical structure of the document
-rather than its visual layout.\vskip 6pt
-Moreover, \LaTeX{} provides a consistent and comprehensive document
-preparation interface. There are simple-to-use commands for
-generating a table of contents, lists of figures and/or tables, and indexes.
-\LaTeX{} can automatically number list entries, equations, figures,
-tables, and footnotes, as well as articles, sections, and subsections.
-Using this numbering system, bibliographic citations, page
-references, and cross references to any other numbered entity (e.g.
-article, section, equation, figure, list entry, etc.) become quite simple
-and straightforward. The use of \LaTeX{} document classes allows
-a simple change of class to transform the appearance of your document.\vskip 6pt
-\LaTeX{} is a powerful tool for managing long and complex documents.
-In particular, partial processing enables long documents to
-be produced article by article without losing sequential information.
-The use of document classes allows a simple change of style
-(or style option) to transform the appearance of your document.
+Cast parts can have small geometric variations from lot-to-lot, therefore it is required to alter the machining CNC code to adapt it to each lot.
+Current practices include human work (long, possible scrap, needs highly trained workers), and automated methods for parts like wind turbines (measurement of the whole part, mini-max/maxi-min optimizations for large free form surfaces).
+The multi operation blank localization method is introduced to focus on drilling and milling scenarios covering a wide range of suitable parts.
+To better understand the package, a short description of the multi operation blank localization algorithm is given.
+The algorithm needs to balance between machining allowance and tolerance error.
+Machining allowance is calculated for each feature as the smallest thickness of the material to be removed.
+Tolerance error is defined for each dimensional tolerance record, that is defined between to features.
+Their distance has a nominal value and upper-lower bounds.
+The goal of the algorithm is to keep the tolerance distances close to the nominal value, while keeping a minimum machining allowance value.
 
-\section{The JuliaCon Article Class}
-\label{sec:documentclass}
+\section{Approach}
+\label{sec:approach}
 %
-The juliacon class file preserves the standard LATEX{} interface such
-that any document that can be produced using the standard LATEX{}
-article class can also be produced with the class file.\vskip 6pt
-It is likely that the make up will change after file submission. For
-this reason, we ask you to ignore details such as slightly long lines,
-page stretching, or figures falling out of synchronization, as these
-details can be dealt with at a later stage.\vskip 6pt
-Use should be made of symbolic references (\verb|\ref| ) in order to
-protect against late changes of order, etc.
+The package needs to support the quick prototyping needs of research, while giving a strong/stable baseline/background to validate the concept in the industry as well (high-level, programozói igények nélkül, amit egy menedzser felsorolna):
 
-\section{USING THE JuliaCon Article CLASS FILE}
+\begin{itemize}
+	\item Model the problem, including geometry representation, qcqp model building and solving, evaluation, visualization.
+	\item Modeling the different behavious of the geometries (holes, planes)
+	\item Handle two basic types of measurements: primitive or free-form.
+	\item Support for importing geometries: all kinds of measurement (expandable/extendable? type system for introducing new measurement types)
+\end{itemize}
+
+Tasks are defined in the workpiece coordinate frame (called workpiece datum).
+Two types of geometries need to be aligned: rough and machined. Currently the algorithm, thus the implementation supports two types of features: holes and planes. 
+A flexible type system is implemented: abstract types are defined and all methods act on them, so implementing a new geometry type (for example to handle point cloud measurement of a rough hole) means defining the type and those methods.
+All other functionality of the package are working automatically: setting up the optimization model, solving it, evaluating the results in details and visualizing the geometries.
+
+\section{Results}
+The following figures show the same part measured with different techniques, such as laser scanner and coordinate measurement arm.
+Based on the package, geometries for both measurement types can be implemented in just a few lines, and the optimization can be run on them.
+Two papers have been published using this tool \cite{cserteg:2023_Annals} for primitive types and \cite{cserteg:2023_CMS} for free-form surfaces.
+
+\section{}
 

### 2024-05-30 paper/prep.rb
update juliacon year

@@ -12,7 +12,7 @@ end
 # ENV variables or default for issue/volume/year
 issue = ENV["JLCON_ISSUE"] === nil ? 1 : ENV["JLCON_ISSUE"]
 volume = ENV["JLCON_VOLUME"] === nil ? 1 : ENV["JLCON_VOLUME"]
-year = ENV["JLCON_YEAR"] === nil ? 2022 : ENV["JLCON_YEAR"]
+year = ENV["JLCON_YEAR"] === nil ? 2023 : ENV["JLCON_YEAR"]
 journal_name = "Proceedings of JuliaCon" # hard-coded for now
 
 open('header.tex', 'w') do |f|

### 2024-05-30 paper/header.tex
write body of paper

@@
 pdftitle = {BlankLocalizationCore.jl: implementing blank localization in Julia},
-pdfsubject = {JuliaCon 2022 Proceedings},
+pdfsubject = {JuliaCon 2023 Proceedings},
 pdfauthor = {Tamás Cserteg, András Kovács, József Váncza},

### 2024-05-30 paper/paper.tex
write body of paper

@@
 Blank localization (also known as workpiece referencing) is an essential task in machining.
-In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely defined/searched.
+In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely established.
 We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a semi-automated way.
-It processes measurement of the rough geometry and the machining CNC code to solve a convex quadratically constrained quadratic program (QCQP).
-It gives an optimal solution for given machining allowance - tolerance error, providing a tool for the machinist to find the appropriate balance between the two.
-The flexibility and extensibility of the Julia language helped the development of this algorithm, materializing in the \pkg{BlankLocalizationCore} package.
+The method processes measurement of the rough geometry and the machining CNC code to solve a convex quadratically constrained quadratic program (QCQP).
+It gives an optimal solution for given machining allowance--tolerance error, providing a tool for the machinist to find the appropriate balance between the two.
+The versatility and extensibility of the Julia language helped the development of this algorithm, materializing in the \texttt{BlankLocalizationCore.jl} package.
 Its flexibility and ease of use make it an excellent research tool, that can be deployed in production as well.
-
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:intro}
+Cast parts may have small geometric variations from lot-to-lot, that need to be addressed before machining by altering the CNC code.
+Current practices include human effort, which takes long time, possibly produces scrap and requires highly trained workers.
+Automated methods exist for complex free-form parts like wind turbines, that are based on the measurement of the rough part and generate the machining code by mini-max/maxi-min optimization (\cite{tan:2014_UnconstrainedApproachBlank}, \cite{ding:2021_CoarsefineOptimizationMethod}).
+Multi operation blank localization was introduced in~\cite{cserteg:2023_Annals} focusing on drilling and milling.
+These machining operations are among the most used ones, therefore the method is applicable for a wide range of products.
+The method and its implementation was developed together, which required a language with support of easy prototyping and wide variety of tools.
+For exactly these reasons chose we the Julia language~\cite{bezanson2017julia}.
 
-Cast parts can have small geometric variations from lot-to-lot, therefore it is required to alter the machining CNC code to adapt it to each lot.
-Current practices include human work (long, possible scrap, needs highly trained workers), and automated methods for parts like wind turbines (measurement of the whole part, mini-max/maxi-min optimizations for large free form surfaces).
-The multi operation blank localization method is introduced to focus on drilling and milling scenarios covering a wide range of suitable parts.
-To better understand the package, a short description of the multi operation blank localization algorithm is given.
-The algorithm needs to balance between machining allowance and tolerance error.
+%TODO: ez túl sok helyet foglal
+\iffalse
+The paper is structured as follows: the multi operation blank localization algorithm is introduced briefly in Sec.~\ref{sec:algo}, followed by the requirements and needs showed up during development in Sec.~\ref{sec:req} and the solutions of those problems in Sec.~\ref{sec:approach}.
+Finally a short example is given in Sec.~\ref{sec:results} and the paper is concluded in Sec.~\ref{sec:conclusion}.
+\fi
+
+\section{Multi operation blank localization}
+\label{sec:algo}
+
+The goal of the algorithm is to find the optimal part zero for each feature group of a workpiece.
+These feature groups could be for example drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
+Features in a feature group can moved only together as a group, but feature groups can be moved separately.
+The to-be-machined features (short: machined features) need to be aligned with the előgyártmány feauterök (called rough features) in a way, that a minimum machining allowance is ensured and the distance tolerance between features is respected.
+Former encodes the requirement, that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of material to be removed.
+The distance tolerance between features is modeled as a lower-upper bound for the distance of two features.
+As feature groups move together, only inter-group tolerances need to be considered.
+Fig.~\ref{fig:hatfig} shows two feature groups with their part zeros as well as the tolerances between features.
+
+\begin{figure}[b]
+	\centerline{\includegraphics[width=0.9\columnwidth]{cirp-annals-2023-figure-2.png}}
+	\caption{Measured part with two machined feature groups and tolerances between them.
+$r^M$ and $r^R$ denote the machined and rough radii of a feature, while $\delta$ the machining allowance \cite{cserteg:2023_Annals}.}
+	\label{fig:hatfig}
+\end{figure}
+
+Inputs of the algorithm are the measurements of the rough part, the machining CNC code for each feature (relative to the corresponding part zero), the tolerance ranges for the features and the minimum machining allowance parameter.
+The output will be the position of the optimal part zeros, where optimal means the lowest average tolerance error at the given allowance value.
+
+Measurements of the rough parts can be obtained with a variety of instruments, including coordinate measurement machines (CMM), laser scanners, measurement arms, etc.
+The two main representations that these devices create are primitive geometries (cylinders, planes, etc.) and free-form geometries in the form of point cloud or triangulated mesh.
+These measurements are fed into the optimization model, which is a convex quadratically constrained quadratic program (QCQP).
+Details of the optimization model can be found in the papers \cite{cserteg:2023_Annals} and \cite{cserteg:2023_CMS}.
+%TODO: ide kéne még egy bekezdés arról, hogy mi is a modell?
+% a mérések alapján -> QCQP ????
+% a free-form / primitive-ről sem írtam még
+
+\iffalse
+The method gives engineers a tool to balance between machining allowance and tolerance error.
+Former is 
 Machining allowance is calculated for each feature as the smallest thickness of the material to be removed.
@@
 The goal of the algorithm is to keep the tolerance distances close to the nominal value, while keeping a minimum machining allowance value.
+\fi
 
@@
 \label{sec:approach}
-%
-The package needs to support the quick prototyping needs of research, while giving a strong/stable baseline/background to validate the concept in the industry as well (high-level, programozói igények nélkül, amit egy menedzser felsorolna):
+
+During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a stable background to validate the concept with our industry partner as well.
+These needs include:
+% (high-level, programozói igények nélkül, amit egy menedzser felsorolna):
 
 \begin{itemize}
-	\item Model the problem, including geometry representation, qcqp model building and solving, evaluation, visualization.
-	\item Modeling the different behavious of the geometries (holes, planes)
-	\item Handle two basic types of measurements: primitive or free-form.
-	\item Support for importing geometries: all kinds of measurement (expandable/extendable? type system for introducing new measurement types)
+	\item A versatile type system for geometry representation. Especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
+	\item Easy-to-use interface for the optimization model.
+	\item Support for importing geometries from a variety of measurement tools (CMM, laser scanner, measurement arm).
+	\item Support for debugging, analyzing and visualizing the results.
+%	\item Handling the differences of drilling and milling (hole and plane geometries).	
+%	\item Model the problem, including geometry representaton, qcqp model building and solving, evaluation, visualization.
+%	\item Modeling the different behavious of the geometries (holes, planes)
+%	\item Handle two basic types of measurements: primitive or free-form.
+%	\item Support for importing geometries: all kinds of measurement (expandable/extendable? type system for introducing new measurement types)
 \end{itemize}
 
+A flexible type system is designed to handle the different representations of geometries and features.
+Abstract hole and plane geometries model the drilling and milling operations, while traits describe if a feature is using a free-form or a primitive representation.
+An internal API (set of functions) is designed to access the relevant properties of the geometries (center point, radius, surface points, etc.).
+
+This internal API is used when constructing the optimization model, utilizing the JuMP ecosystem~\cite{Lubin2023}.
+With JuMP's excellent design, coding the optimization model was as easy as repeating the mathematical model in Julia.
+Other advantage of the JuMP ecosystem is, that solvers can be easily swapped out if needed.
+For development, the FICO Xpress solver was used (with academic license), but our industry partner could use the Ipopt or SCIP solvers without issue.
+Using the internal API gives the advantage, that new geometry representations can be quickly used with the optimization model by just implementing a new type and a set of functions.
+
+As mentioned earlier, important requirement was to handle the output formats of many different devices.
+Every measurement instrument comes with its own processing software and export formats, not necessarily designed for interoperability.
+As a result, we needed to write (or use) parsers for different text and tabular formats.
+%The measurement results are read into their own respective type that implements the internal API, which means that
+
+The geometric computations are implemented with the help of the \texttt{Meshes.jl} package, which enabled us to easily visualize the geometries and results from the beginnings.
+See Fig.~\ref{fig:hatfig} for an example.
+
+\iffalse
 Tasks are defined in the workpiece coordinate frame (called workpiece datum).
@@
 All other functionality of the package are working automatically: setting up the optimization model, solving it, evaluating the results in details and visualizing the geometries.
+\fi
 
-\section{Results}
-The following figures show the same part measured with different techniques, such as laser scanner and coordinate measurement arm.
-Based on the package, geometries for both measurement types can be implemented in just a few lines, and the optimization can be run on them.
-Two papers have been published using this tool \cite{cserteg:2023_Annals} for primitive types and \cite{cserteg:2023_CMS} for free-form surfaces.
+\section{Results and future work} %TODO: or Example
+\label{sec:results}
 
-\section{}
+Fig.~\ref{fig:pareto} shows the allowance-tolerance pairs for an experiment from our paper.
 
-If the file \verb|juliacon.cls|  is not already in the appropriate system directory
-for \LaTeX{} files, either arrange for it to be put there or copy
-it to your working directory. The \verb|juliacon|  document class is implemented
-as a complete class, not a document style option. In order to
-use the \verb|juliacon  document class, replace \verb|article|  by \verb|juliacon|  in the
-\verb|\documentclass|  command at the beginning of your document:
-\vskip 6pt
-\begin{centering}
-    \verb|\documentclass{article}|  \end{centering}
-\vskip 6pt
-replace by
-\vskip 6pt
- \verb|\documentclass{juliacon}|  \vskip 6pt
-In general, the following standard document \verb|style|  options should
-{ \itshape not} be used with the {\footnotesize \itshape article} class file:
-\begin{enumerate}
-\item[(1)] \verb|10pt|,  \verb|11pt|,  \verb|12pt|   ? unavailable;
-\item[(2)] \verb|twoside|  (no associated style file) ? \verb|twoside|  is the default;
-\item[(3)] \verb|fleqn|, \verb|leqno|, \verb|titlepage| ? should not be used;
-\end{enumerate}
-
-\section{Additional Document Style Options}
-\label{sec:additional_doc}
-%
-The following additional style option is available with the \verb|juliacon|  class file:
-\vskip 6pt
-Please place any additional command definitions at the very start of
-the \LaTeX{} file, before the \verb|\begin{document}|. For example, user-defined
-\verb|\def|  and \verb|\newcommand|   commands that define macros for
-technical expressions should be placed here. Other author-defined
-macros should be kept to a minimum.
-\vskip 6pt
-Commands that differ from the standard \LaTeX{} interface, or that
-are provided in addition to the standard interface, are explained in
-this guide. This guide is not a substitute for the \LaTeX{} manual itself.
-Authors planning to submit their papers in \LaTeX{} are advised to use
-\verb|juliacon.cls|  as early as possible in the creation of their files.
-
-%
-%
-%
-%
-\begin{table*}[t]
-\tabcolsep22pt
-\tbl{If necessary, the tables can be extended both columns.}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Test 1 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test 2 & Testing Data I & & 105\\\hline
-Test 3 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\label{tab:symbols}
-\begin{tabnote}
-This is an example of table footnote.
-\end{tabnote}
-\end{table*}
-% \begin{figure*}[t]
-% \centerline{\includegraphics[width=11cm]{juliagraphs.png}}
-% \caption{If necessary, the images can be extended both columns.}
-%   \label{fig:sample_image}
-% \end{figure*}
-
-\section{Additional features}
-\label{sec:additional_faci}
-In addition to all the standard \LaTeX{} design elements, the \verb|juliacon|  class file includes the following features:
-In general, once you have used the additional \verb|juliacon.cls| facilities
-in your document, do not process it with a standard \LaTeX{} class
-file.
-
-\subsection{Titles, Author's Name, and Affiliation}
-\label{subsub:title_auth}
-The title of the article, author's name, and affiliation are used at the
-beginning of the article (for the main title). These can be produced
-using the following code:
-
-\begin{verbatim}
-\title{ This is an example of article title} }
-\author{
-   \large 1st Author \\[-3pt]
-   \normalsize 1st author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	1st author's email address \\[-3pt]
-  \and
-   \large 2nd Author \\[-3pt]
-   \normalsize 2nd author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	2nd author's email address \\[-3pt]
-\and
-   \large 3rd Author \\[-3pt]
-   \normalsize 3rd author's affiliation  \\[-3pt]
-    \normalsize 1st line of address \\[-3pt]
-    \normalsize 2nd line of address \\[-3pt]
-    \normalsize	3rd author's email address \\[-3pt]
-}
-\maketitle
-\end{verbatim}
-
-\subsection{Writing Julia code}
-
-A special environment is already defined for Julia code,
-built on top of \textit{listings} and \textit{jlcode}.
-
-\begin{verbatim}
-\begin{lstlisting}[
-    language = Julia, 
-    numbers=left, 
-    label={lst:exmplg}, 
-    caption={Example Code Block.}
-]
-using Plots
-
-x = -3.0:0.01:3.0
-y = rand(length(x))
-plot(x, y)
-\end{lstlisting}
-\end{verbatim}
-\begin{lstlisting}[
-    language = Julia, 
-    numbers=left, 
-    label={lst:exmplg}, 
-    caption={Example Code Block.}
-]
-using Plots
-
-x = -3.0:0.01:3.0
-y = rand(length(x))
-plot(x, y)
-\end{lstlisting}
-
-\subsection{Abstracts, Key words, term etc...}
-\label{subsub:abs_key_etc}
-
-At the beginning of your article, the title should be generated
-in the usual way using the \verb|\maketitle|  command. For genaral tem and keywords use
-\verb|\terms|,
-\verb|\keywords|  commands respectively. The abstract should be enclosed
-within an abstract environment, All these environment
-can be produced using the following code:
-\begin{verbatim}
-\terms{Experimentation, Human Factors}
-
-\keywords{Face animation, image-based modelling...}
-
-\begin{abstract}
-In this paper, we propose a new method for the
-systematic determination of the model's base of
-time varying delay system. This method based on
-the construction of the classification data related
-to the considered system. The number, the orders,
-the time delay and the parameters of the local
-models are generated automatically without any
-knowledge about the full operating range of the
-process. The parametric identification of the local
-models is realized by a new recursive algorithm for
-on line identification of systems with unknown time
-delay. The proposed algorithm allows simultaneous
-estimation of time delay and parameters of
-discrete-time systems. The effectiveness of
-the new method has been illustrated through
-simulation.
-\end{abstract}
-
-\end{verbatim}
-
-\section{Some guidelines}
-\label{sec:some_guide}
-The following notes may help you achieve the best effects with the
-\verb|juliacon|  class file.
-
-\subsection{Sections}
-\label{subsub:sections}
-\LaTeXe{}  provides four levels of section headings and they are all
-defined in the \verb|juliacon|  class file:
-\begin{itemize}
-\item \verb|\section|
-\item \verb|\subsection|
-\item \verb|\subsubsection|
-\item \verb|\paragraph|
-\end{itemize}
-Section headings are automatically converted to allcaps style.
-\subsection{Lists}
-\label{sec:lists}
-%
-The \verb|juliacon|   class file provides unnumbered lists using the
-\verb|unnumlist|  environment for example,
-
-\begin{unnumlist}
-\item First unnumbered item which has no label and is indented from the
-left margin.
-\item Second unnumbered item.
-\item Third unnumbered item.
-\end{unnumlist}
-The unnumbered list which has no label and is indented from the
-left margin. was produced by:
-\begin{verbatim}
-\begin{unnumlist}
-\item First unnumbered item...
-\item Second unnumbered item...
-\item Third unnumbered item...
-\end{unnumlist}
-\end{verbatim}
-
-The \verb|juliacon|  class file also provides hyphen list using the
-\verb|itemize|  environment for example,
-\begin{itemize}
-\item First unnumbered bulleted item which has no label and is indented
-from the left margin.
-\item Second unnumbered bulleted item.
-\item Third unnumbered bulleted item which has no label and is indented
-from the left margin.
-\end{itemize}
-was produced by:
-\begin{verbatim}
-\begin{itemize}
-\item First item...
-\item Second item...
-\item Third item...
-\end{itemize}
-\end{verbatim}
-
-Numbered list is also provided in acmtog class file using the
-enumerate environment for example,
-\begin{enumerate}
-\item The attenuated and diluted stellar radiation.
-\item Scattered radiation, and
-\item Reradiation from other grains.
-\end{enumerate}
-
-was produced by:
-\begin{verbatim}
-\begin{enumerate}
-\item The attenuated...
-\item Scattered radiation, and...
-\item Reradiation from other grains...
-\end{enumerate}
-\end{verbatim}
-\subsection{Illustrations (or figures)}
-\label{subsub:sec_Illus}
-The \verb|juliacon|  class file will cope with most of the positioning of
-your illustrations and you should not normally use the optional positional
-qualifiers on the \verb|figure|  environment that would override
-these decisions.
-\vskip 6pt
-
-%
-\begin{figure}[t]
-\centerline{\includegraphics[width=4cm]{juliagraphs.png}}
-\caption{This is example of the image in a column.}
-	\label{fig:sample_figure}
+\begin{figure}[b]
+	\centerline{\includegraphics[width=0.9\columnwidth]{pareto-new-label.png}}
+	\caption{Balancing the machining allowance and the tolerance error \cite{cserteg:2023_Annals}.}
+	\label{fig:pareto}
 \end{figure}
 
-The figure \ref{fig:sample_figure} is taken from the JuliaGraphs
-organization \footnote{https://github.com/JuliaGraphs}.
+Preliminary results were first published in \cite{cserteg:2023_DigitalTwinAssisted}.
+A journal paper describes the original algorithm \cite{cserteg:2023_Annals}, and a conference paper details the modifications for free-form surfaces \cite{cserteg:2023_CMS}.
 
-Figure captions should be \emph{below} the figure itself, therefore the
-\verb|\caption|  command should appear after the figure or space left for
-an illustration. For example, Figure 1 is produced using the following
-commands:
+Future plans for the package and the method itself include an overhaul of the tolerance modeling scheme.
+Currently only dimensional tolerances are handled, but it should be discovered if more GD\&T tolerances can be incorporated into the model.
+The methodology currently only supports cylinders and planes, thus drilling and milling.
+It is a future research direction to extend the handled machining operations for example to turning.
 
-\begin{verbatim}
-\begin{figure}
-\centerline{\includegraphics[width=20pc]{Graphics.eps}}
-\caption{An example of the testing process for a
-binary tree. The globa null hypothesis is tested
-first at level $\alpha$ (a), and the level of
-individual variables is reached last (d). Note
-that individual hypotheses can be tested at
-level $\alpha/4$ and not $\alpha/8$ as one might
-expect at first.}
-\label{sample-figure_2}
-\end{figure}
-\end{verbatim}
-Figures can be resized using first and second argument of
-\verb|\includegraphics|   command. First argument is used for modifying
-figure height and the second argument is used for modifying
-figure width respectively.
-\vskip 6pt
-Cross-referencing of figures, tables, and numbered, displayed
-equations using the \verb|\label|  and \verb|\ref|   commands is encouraged.
-For example, in referencing Figure 1 above, we used
-\verb|Figure~\ref{sample-figure}|
+%TODO: future works
+% - tolerance modeling
+% - discover other machining operations (turning)
+% - add more examples to docs
 
- \subsection{Tables}
-\label{subsub:sec_Tab}
-The \verb|juliacon|   class file will cope with most of the positioning of
-your tables and you should not normally use the optional positional qualifiers on the table environment which would override these
-decisions. Table captions should be at the top.
-\begin{verbatim}
-\begin{table}
-\tbl{Tuning Set and Testing Set}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Train70 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test70 & Testing Data I & & 105\\\hline
-Test30 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\end{table}
-\end{verbatim}
-
-\begin{table}
-\tbl{Tuning Set and Testing Set}{
-\begin{tabular}{|l|l|c|c|}\hline
-Label & \multicolumn{1}{c|}{Description}
-& Number of Users &
-Number of Queries\\\hline
-Test 1 & Training Data &
-\smash{\raise-7pt\hbox{70}} & 104\\
-\cline{1-2}\cline{4-4}
-Test 2 & Testing Data I & & 105\\\hline
-Test 3 & Testing Data II & 30 & 119\\\hline
-& Total & 100 & 328\\\hline
-\end{tabular}}
-\end{table}
-\subsection{Landscaping Pages}
-\label{subsub:landscaping_pages}
-If a table is too wide to fit the standard measure, it may be turned,
-with its caption, to 90 degrees. Landscape tables cannot be produced
-directly using the \verb|juliacon|   class file because \TeX{} itself cannot
-turn the page, and not all device drivers provide such a facility.
-The following procedure can be used to produce such pages.
-\vskip 6pt
-Use the package \verb|rotating|   in your document and change the coding
-from
-\begin{verbatim}
-\begin{table}...\end{table}
-to
-\begin{sidewaystable}...\end{sidewaystable}
-and for figures
-\begin{figure}...\end{figure}
-to
-\begin{sidewaysfigure}...\end{sidewaysfigure}
-\end{verbatim}
-
-environments in your document to turn your table on the appropriate
-page of your document. For instance, the following code prints
-a page with the running head, a message half way down and the
-table number towards the bottom.
-\begin{verbatim}
-\begin{sidewaystable}
-\tbl{Landscape table caption to go here.}{...}
-\label{landtab}
-\end{sidewaystable}
-\end{verbatim}
-
-\subsection{Double Column Figure and Tables}
-\label{subsub:double_fig_tab}
-For generating the output of figures and tables in double column
-we can use the following coding:
-
-\begin{enumerate}
-\item For Figures:
-\begin{verbatim}
-\begin{figure*}...\end{figure*}
-\end{verbatim}
-\item For landscape figures:
-\begin{verbatim}
-\begin{sidewaysfigure*}...\end{sidewaysfigure*}
-\end{verbatim}
-\item For Tables:
-\begin{verbatim}
-\begin{table*}...\end{table*}
-\end{verbatim}
-\item For landscape tables:
-\begin{verbatim}
-\begin{sidewaystable*}...\end{sidewaystable*}
-\end{verbatim}
-\end{enumerate}
-
-\subsection{Typesetting Mathematics}
-\label{subsub:type_math}
-The \verb|juliacon| class file will set displayed mathematics with center to
-the column width, provided that you use the \LaTeXe{} standard of
-open and closed square brackets as delimiters.
-The equation
-\[
-\sum_{i=1}^p \lambda_i = (S)
-\]
-
-was typeset using the acmtog class file with the commands
-
-\begin{verbatim}
-\[
-\sum_{i=1}^p \lambda_i = (S)
-\]
-\end{verbatim}
-
-For display equations, cross-referencing is encouraged. For example,
-\begin{verbatim}
-\begin{equation}
-(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
-\label{eq:samplevar}
-\end{equation}
-Equation~(\ref{eq:samplevar}) gives the formula for
-sample variance.
-\end{verbatim}
-The following output is generated with the above coding:
-\begin{equation}
-(n-1)^{-1} \sum^n_{i=1} (X_i - \overline{X})^2.
-\label{eq:samplevar}
-\end{equation}
-Equation~(\ref{eq:samplevar}) gives the formula for
-sample variance.
-
-\subsection{Enunciations}
-\label{subsub:enunciation}
-The \verb|juliacon|   class file generates the enunciations with the help of
-the following commands:
-\begin{verbatim}
-\begin{theorem}...\end{theorem}
-\begin{strategy}...\end{strategy}
-\begin{property}...\end{property}
-\begin{proposition}...\end{proposition}
-\begin{lemma}...\end{lemma}
-\begin{example}...\end{example}
-\begin{proof}...\end{proof}
-\begin{definition}...\end{definition}
-\begin{algorithm}...\end{algorithm}
-\begin{remark}...\end{remark}
-\end{verbatim}
-The above-mentioned coding can also include optional arguments
-such as
-\begin{verbatim}
-\begin{theorem}[...]. Example for theorem:
-\begin{theorem}[Generalized Poincare Conjecture]
-Four score and seven ... created equal.
-\end{theorem}
-\end{verbatim}
-
-\begin{theorem}[Generalized Poincare Conjecture]
-Four score and seven years ago our fathers brought forth,
-upon this continent, a new nation, conceived in Liberty,
- and dedicated to the proposition that all men are
-created equal.
-\end{theorem}
-
-\subsection{Extract}
-\label{subsub:extract}
-Extract environment should be coded within
-\begin{verbatim}
-\begin{extract}..\end{extract}
-\end{verbatim}
-
-\subsection{Balancing column at last page}
-\label{subsub:Balance}
-For balancing the both column length at last page use :
-\begin{verbatim}
-\vadjust{\vfill\pagebreak}
-\end{verbatim}
-
-%\vadjust{\vfill\pagebreak}
-
-at appropriate place in your \TeX{} file or in bibliography file.
-
-\section{Handling references}
-\label{subsub:references}
-References are most easily (and correctly) generated using the
-BIBTEX, which is easily invoked via
-\begin{verbatim}
-\bibliographystyle{juliacon}
-\bibliography{ref}
-\end{verbatim}
-When submitting the document source (.tex) file to external
-parties, the ref.bib file should be sent with it.
-\cite{bezanson2017julia}
+\section{Acknowledgments}
+%TODO: CMS másolása
+This research has been supported by the National Laboratory for Autonomous Systems RRF-2.3.1-21-2022-00002 and the ED\_18-2-2018-0006 grants of the NRDIO.
 

### 2024-05-31 paper/paper.tex
incorporate review suggestions

@@
 Blank localization (also known as workpiece referencing) is an essential task in machining. 
-In this step the geometric relation of the tool of a machine (mill, lathe etc.) and the workpiece(s) needs to be precisely established.
-We introduced the concept of multi operation blank localization to address this task for drilling and milling scenarios in a semi-automated way.
-The method processes measurement of the rough geometry and the machining CNC code to solve a convex quadratically constrained quadratic program (QCQP).
-It gives an optimal solution for given machining allowance--tolerance error, providing a tool for the machinist to find the appropriate balance between the two.
+It aims to precisely establish the geometric relation of the a machine tool (mill, lathe etc.) and the workpiece.
+We introduced the concept of multi-operation blank localization to address this task for drilling and milling scenarios in a semi-automated way, which allows positioning different machining features (e.g., different holes) separately in order to exploit the tolerances on the relative position of those features to compensate the small errors of the blank.
+The method takes as input the measured rough geometry and the machining CNC code, and computes the best possible position of each feature considering machining allowances and tolerances by solving a convex quadratically constrained quadratic program (QCQP).
 The versatility and extensibility of the Julia language helped the development of this algorithm, materializing in the \texttt{BlankLocalizationCore.jl} package.
-Its flexibility and ease of use make it an excellent research tool, that can be deployed in production as well.
+Its flexibility and ease of use make it an excellent research tool that can be deployed in production as well.
 \end{abstract}
@@
 \label{sec:intro}
-Cast parts may have small geometric variations from lot-to-lot, that need to be addressed before machining by altering the CNC code.
-Current practices include human effort, which takes long time, possibly produces scrap and requires highly trained workers.
-Automated methods exist for complex free-form parts like wind turbines, that are based on the measurement of the rough part and generate the machining code by mini-max/maxi-min optimization (\cite{tan:2014_UnconstrainedApproachBlank}, \cite{ding:2021_CoarsefineOptimizationMethod}).
-Multi operation blank localization was introduced in~\cite{cserteg:2023_Annals} focusing on drilling and milling.
+Cast parts may have small geometric variations from lot to lot that need to be addressed before machining by altering the CNC code.
+Current practice is dominated by iterative adjustments by the human operator, which requires highly trained workers, takes a long time, and still, may produce scrap.
+Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object 
+%based on the measurement of the rough part and generate the machining code by mini-max/maxi-min optimization 
+\cite{tan:2014_UnconstrainedApproachBlank}\cite{ding:2021_CoarsefineOptimizationMethod}).
+Multi-operation blank localization was introduced in~\cite{cserteg:2023_Annals} focusing on drilling and milling.
 These machining operations are among the most used ones, therefore the method is applicable for a wide range of products.
-The method and its implementation was developed together, which required a language with support of easy prototyping and wide variety of tools.
-For exactly these reasons chose we the Julia language~\cite{bezanson2017julia}.
+The abstract method and its implementation was developed in parallel, which required a language with support for easy prototyping and wide variety of tools.
+Exactly for these reasons we chose the Julia language~\cite{bezanson2017julia}.
 
@@
 
-\section{Multi operation blank localization}
+\section{Multi-operation blank localization}
 \label{sec:algo}
 
-The goal of the algorithm is to find the optimal part zero for each feature group of a workpiece.
-These feature groups could be for example drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
-Features in a feature group can moved only together as a group, but feature groups can be moved separately.
-The to-be-machined features (short: machined features) need to be aligned with the előgyártmány feauterök (called rough features) in a way, that a minimum machining allowance is ensured and the distance tolerance between features is respected.
-Former encodes the requirement, that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of material to be removed.
-The distance tolerance between features is modeled as a lower-upper bound for the distance of two features.
+The algorithm looks for the optimal position (part zero) for each feature group on the workpiece. 
+Features within a group can be, for example, drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
+Features within the same group must be moved together, but different feature groups can be moved separately.
+The to-be-machined features (short: machined features) need to be aligned with the features on the blank (called rough features) in a way that a minimum machining allowance is ensured and the dimensional tolerances between features are respected.
+The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of the material removed.
+A dimensional tolerance between two features is modeled as a lower and upper bounds on the distance between the two features.
 As feature groups move together, only inter-group tolerances need to be considered.
-Fig.~\ref{fig:hatfig} shows two feature groups with their part zeros as well as the tolerances between features.
+Fig.~\ref{fig:hatfig} shows two feature groups with their part zeros, as well as the tolerances between features.
 
@@
 
-Inputs of the algorithm are the measurements of the rough part, the machining CNC code for each feature (relative to the corresponding part zero), the tolerance ranges for the features and the minimum machining allowance parameter.
-The output will be the position of the optimal part zeros, where optimal means the lowest average tolerance error at the given allowance value.
+Inputs of the algorithm are the measured geometry of the rough part, the machining CNC code for each feature (relative to the corresponding part zero), the tolerance ranges for the features, and the minimum machining allowance parameter.
+The output is the optimal position of the part zeros, where optimal means the lowest average tolerance error subject to a given machining allowance.
 
@@
 
-\section{Approach}
+\section{Implementation in Julia}
+%\section{Approach}
 \label{sec:approach}
@@
 \begin{itemize}
-	\item A versatile type system for geometry representation. Especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
+	\item A versatile type system for geometrical representation, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
 	\item Easy-to-use interface for the optimization model.
@@
 A flexible type system is designed to handle the different representations of geometries and features.
-Abstract hole and plane geometries model the drilling and milling operations, while traits describe if a feature is using a free-form or a primitive representation.
-An internal API (set of functions) is designed to access the relevant properties of the geometries (center point, radius, surface points, etc.).
+Abstract hole and plane geometries model the drilling and milling operations, while traits describe if a feature uses a free-form or a primitive representation.
+An internal API (set of functions) is designed to access the relevant properties of the geometries (center point, radius, surface points, etc).
 
-This internal API is used when constructing the optimization model, utilizing the JuMP ecosystem~\cite{Lubin2023}.
+This internal API is used when constructing the optimization model utilizing the JuMP ecosystem~\cite{Lubin2023}.
 With JuMP's excellent design, coding the optimization model was as easy as repeating the mathematical model in Julia.
-Other advantage of the JuMP ecosystem is, that solvers can be easily swapped out if needed.
+Other advantage of the JuMP ecosystem is that solvers can be easily swapped if needed.
 For development, the FICO Xpress solver was used (with academic license), but our industry partner could use the Ipopt or SCIP solvers without issue.
-Using the internal API gives the advantage, that new geometry representations can be quickly used with the optimization model by just implementing a new type and a set of functions.
+Using the internal API gives the advantage that new geometry representations can be quickly used with the optimization model by just implementing a new type and a set of functions.
 
-As mentioned earlier, important requirement was to handle the output formats of many different devices.
+As mentioned earlier, an important requirement was to handle the output formats of many different devices.
 Every measurement instrument comes with its own processing software and export formats, not necessarily designed for interoperability.
@@
 
-The geometric computations are implemented with the help of the \texttt{Meshes.jl} package, which enabled us to easily visualize the geometries and results from the beginnings.
-See Fig.~\ref{fig:hatfig} for an example.
+The geometric computations are implemented with the help of the \texttt{Meshes.jl} package, which enabled us to easily visualize the geometries and results from the beginnings, see Fig.~\ref{fig:hatfig} for an example.
 
@@
 
-Fig.~\ref{fig:pareto} shows the allowance-tolerance pairs for an experiment from our paper.
+Fig.~\ref{fig:pareto} shows the allowance-tolerance pairs for an experiment from \cite{cserteg:2023_Annals}.
+The diagram illustrates that the proposed algorithm (blue curve) leads to lower tolerance errors for any given machining allowance than earlier approaches, and it can also ensure significantly larger machining allowance.
+Obviously, there is a trade-off between small tolerance error and large machining allowance.
+Preliminary results were first published in \cite{cserteg:2023_DigitalTwinAssisted}.
+A journal paper describes the original algorithm \cite{cserteg:2023_Annals}, and a conference paper details the modifications for free-form surfaces \cite{cserteg:2023_CMS}.
 
@@
 
-Preliminary results were first published in \cite{cserteg:2023_DigitalTwinAssisted}.
-A journal paper describes the original algorithm \cite{cserteg:2023_Annals}, and a conference paper details the modifications for free-form surfaces \cite{cserteg:2023_CMS}.
-
 Future plans for the package and the method itself include an overhaul of the tolerance modeling scheme.
-Currently only dimensional tolerances are handled, but it should be discovered if more GD\&T tolerances can be incorporated into the model.
-The methodology currently only supports cylinders and planes, thus drilling and milling.
-It is a future research direction to extend the handled machining operations for example to turning.
+Currently, only dimensional tolerances are handled, but it should be discovered if more GD\&T tolerances can be incorporated into the model.
+The current implementation supports only cylinders and planes, thus drilling and milling; it is a future research direction to extend the handled machining operations, e.g., to turning.
 
@@
 %TODO: CMS másolása
-This research has been supported by the National Laboratory for Autonomous Systems RRF-2.3.1-21-2022-00002 and the ED\_18-2-2018-0006 grants of the NRDIO.
+This research has been supported by the National Laboratory for Autonomous Systems RRF-2.3.1-21-2022-00002 and the NRDIO TKP2021-NKTA-01 grants.
 

### 2024-05-31 paper/paper.tex
small updates to text

@@
 Blank localization (also known as workpiece referencing) is an essential task in machining. 
-It aims to precisely establish the geometric relation of the a machine tool (mill, lathe etc.) and the workpiece.
+It aims to precisely establish the geometric relation of the machine tool (mill, lathe, etc.) and the workpiece.
 We introduced the concept of multi-operation blank localization to address this task for drilling and milling scenarios in a semi-automated way, which allows positioning different machining features (e.g., different holes) separately in order to exploit the tolerances on the relative position of those features to compensate the small errors of the blank.
@@
 Current practice is dominated by iterative adjustments by the human operator, which requires highly trained workers, takes a long time, and still, may produce scrap.
-Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object 
-%based on the measurement of the rough part and generate the machining code by mini-max/maxi-min optimization 
-\cite{tan:2014_UnconstrainedApproachBlank}\cite{ding:2021_CoarsefineOptimizationMethod}).
+Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object (\cite{tan:2014_UnconstrainedApproachBlank}\cite{ding:2021_CoarsefineOptimizationMethod}).
 Multi-operation blank localization was introduced in~\cite{cserteg:2023_Annals} focusing on drilling and milling.
@@
 The to-be-machined features (short: machined features) need to be aligned with the features on the blank (called rough features) in a way that a minimum machining allowance is ensured and the dimensional tolerances between features are respected.
-The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of the material removed.
-A dimensional tolerance between two features is modeled as a lower and upper bounds on the distance between the two features.
+The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of removed material.
+A dimensional tolerance between two features is modeled as lower and upper bounds on the distance between the two features.
 As feature groups move together, only inter-group tolerances need to be considered.
@@
 \begin{figure}[b]
-	\centerline{\includegraphics[width=0.9\columnwidth]{cirp-annals-2023-figure-2.png}}
+	\centerline{\includegraphics[width=0.95\columnwidth]{cirp-annals-2023-figure-2.png}}
 	\caption{Measured part with two machined feature groups and tolerances between them.
@@
 
-During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a stable background to validate the concept with our industry partner as well.
+During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner as well.
 These needs include:
@@
 Abstract hole and plane geometries model the drilling and milling operations, while traits describe if a feature uses a free-form or a primitive representation.
-An internal API (set of functions) is designed to access the relevant properties of the geometries (center point, radius, surface points, etc).
+An internal API (set of functions) is designed to access the relevant properties of the geometries (center point, radius, surface points, etc.).
 
@@
 
-\begin{figure}[b]
-	\centerline{\includegraphics[width=0.9\columnwidth]{pareto-new-label.png}}
+\begin{figure}[t]
+	\centerline{\includegraphics[width=0.95\columnwidth]{pareto-new-label.png}}
 	\caption{Balancing the machining allowance and the tolerance error \cite{cserteg:2023_Annals}.}
@@
 \section{Acknowledgments}
-%TODO: CMS másolása
-This research has been supported by the National Laboratory for Autonomous Systems RRF-2.3.1-21-2022-00002 and the NRDIO TKP2021-NKTA-01 grants.
+The research was supported by the European Union within the framework of the National Laboratory for Autonomous Systems (RRF-2.3.1-21-2022-00002) and the NRDIO TKP2021-NKTA-01 grants.
 

### 2024-05-31 paper/paper.tex
remove comments

@@
 
-%TODO: ez túl sok helyet foglal
-\iffalse
-The paper is structured as follows: the multi operation blank localization algorithm is introduced briefly in Sec.~\ref{sec:algo}, followed by the requirements and needs showed up during development in Sec.~\ref{sec:req} and the solutions of those problems in Sec.~\ref{sec:approach}.
-Finally a short example is given in Sec.~\ref{sec:results} and the paper is concluded in Sec.~\ref{sec:conclusion}.
-\fi
-
 \section{Multi-operation blank localization}
@@
 Details of the optimization model can be found in the papers \cite{cserteg:2023_Annals} and \cite{cserteg:2023_CMS}.
-%TODO: ide kéne még egy bekezdés arról, hogy mi is a modell?
-% a mérések alapján -> QCQP ????
-% a free-form / primitive-ről sem írtam még
-
-\iffalse
-The method gives engineers a tool to balance between machining allowance and tolerance error.
-Former is
-Machining allowance is calculated for each feature as the smallest thickness of the material to be removed.
-Tolerance error is defined for each dimensional tolerance record, that is defined between to features.
-Their distance has a nominal value and upper-lower bounds.
-The goal of the algorithm is to keep the tolerance distances close to the nominal value, while keeping a minimum machining allowance value.
-\fi
 
 \section{Implementation in Julia}
-%\section{Approach}
 \label{sec:approach}
@@
 These needs include:
-% (high-level, programozói igények nélkül, amit egy menedzser felsorolna):
 
@@
 	\item Support for debugging, analyzing and visualizing the results.
-%	\item Handling the differences of drilling and milling (hole and plane geometries).	
-%	\item Model the problem, including geometry representaton, qcqp model building and solving, evaluation, visualization.
-%	\item Modeling the different behavious of the geometries (holes, planes)
-%	\item Handle two basic types of measurements: primitive or free-form.
-%	\item Support for importing geometries: all kinds of measurement (expandable/extendable? type system for introducing new measurement types)
 \end{itemize}
@@
 As a result, we needed to write (or use) parsers for different text and tabular formats.
-%The measurement results are read into their own respective type that implements the internal API, which means that
 
@@
 
-\iffalse
-Tasks are defined in the workpiece coordinate frame (called workpiece datum).
-Two types of geometries need to be aligned: rough and machined. Currently the algorithm, thus the implementation supports two types of features: holes and planes.
-A flexible type system is implemented: abstract types are defined and all methods act on them, so implementing a new geometry type (for example to handle point cloud measurement of a rough hole) means defining the type and those methods.
-All other functionality of the package are working automatically: setting up the optimization model, solving it, evaluating the results in details and visualizing the geometries.
-\fi
-
-\section{Results and future work} %TODO: or Example
+\section{Results and future work}
 \label{sec:results}
@@
 
-%TODO: future works
-% - tolerance modeling
-% - discover other machining operations (turning)
-% - add more examples to docs
-
 \section{Acknowledgments}

### 2024-05-31 paper/paper.tex
update citation orders and acknowledgement text

@@
 Current practice is dominated by iterative adjustments by the human operator, which requires highly trained workers, takes a long time, and still, may produce scrap.
-Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object (\cite{tan:2014_UnconstrainedApproachBlank}\cite{ding:2021_CoarsefineOptimizationMethod}).
+Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object (\cite{ding:2021_CoarsefineOptimizationMethod}\cite{tan:2014_UnconstrainedApproachBlank}).
 Multi-operation blank localization was introduced in~\cite{cserteg:2023_Annals} focusing on drilling and milling.
@@
 These measurements are fed into the optimization model, which is a convex quadratically constrained quadratic program (QCQP).
-Details of the optimization model can be found in the papers \cite{cserteg:2023_Annals} and \cite{cserteg:2023_CMS}.
+Details of the optimization model can be found in the papers \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}.
 
@@
 \section{Acknowledgments}
-The research was supported by the European Union within the framework of the National Laboratory for Autonomous Systems (RRF-2.3.1-21-2022-00002) and the NRDIO TKP2021-NKTA-01 grants.
+The research was supported by the European Union within the framework of the National Laboratory for Autonomous Systems (RRF-2.3.1-21-2022-00002) and the TKP2021-NKTA-01  NRDIO grant on "Research on cooperative production and logistics systems to support a competitive and sustainable economy".
 

### 2025-03-31 paper/paper.tex
rework sec 2 as per review

@@
 
-The algorithm looks for the optimal position (part zero) for each feature group on the workpiece. 
+The algorithm looks for the optimal position for each feature group on the workpiece.
 Features within a group can be, for example, drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
-Features within the same group must be moved together, but different feature groups can be moved separately.
-The to-be-machined features (short: machined features) need to be aligned with the features on the blank (called rough features) in a way that a minimum machining allowance is ensured and the dimensional tolerances between features are respected.
-The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of removed material.
-A dimensional tolerance between two features is modeled as lower and upper bounds on the distance between the two features.
-As feature groups move together, only inter-group tolerances need to be considered.
-Fig.~\ref{fig:hatfig} shows two feature groups with their part zeros, as well as the tolerances between features.
+Features within the same group move together, but different feature groups can be moved separately.
+The to-be-machined features (short: machined features) need to "enclose" the features on the blank (called rough features) with a minimum machining allowance which ensures the required surface finish.
+While doing so, the dimensional tolerances between some features need to be respected, as these describe functional properties (e.g. connections to other mating parts).
+Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals} shows an example of these features.
 
-\begin{figure}[b]
+\begin{figure}[hbt]
 	\centerline{\includegraphics[width=0.95\columnwidth]{cirp-annals-2023-figure-2.png}}
-	\caption{Measured part with two machined feature groups and tolerances between them.
+	\caption{3D scanned rough features (in grey), two machined feature groups with their part zeros (orange and purple), and tolerances that connect some features \cite{cserteg:2023_Annals}.}
+	%\caption{Measured part with two machined feature groups and tolerances between them.
 $r^M$ and $r^R$ denote the machined and rough radii of a feature, while $\delta$ the machining allowance \cite{cserteg:2023_Annals}.}
@@
 
-Inputs of the algorithm are the measured geometry of the rough part, the machining CNC code for each feature (relative to the corresponding part zero), the tolerance ranges for the features, and the minimum machining allowance parameter.
-The output is the optimal position of the part zeros, where optimal means the lowest average tolerance error subject to a given machining allowance.
+%The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of removed material.
+%A dimensional tolerance between two features is modeled as lower and upper bounds on the distance between the two features.
+%As feature groups move together, only inter-group tolerances need to be considered.
 
-Measurements of the rough parts can be obtained with a variety of instruments, including coordinate measurement machines (CMM), laser scanners, measurement arms, etc.
-The two main representations that these devices create are primitive geometries (cylinders, planes, etc.) and free-form geometries in the form of point cloud or triangulated mesh.
-These measurements are fed into the optimization model, which is a convex quadratically constrained quadratic program (QCQP).
-Details of the optimization model can be found in the papers \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}.
+%Briefly we can summarize the multi-operation blank localization as a method that aligns the machined and rough geometries with the required minimum overlap.
+%It does it while making sure that features that are connected by dimensional tolerances are within the required distance range.
+
+%Tolerance model is used
+%Geometric computations
+%Those two are bundled in a convex optimization problem.
+The developed tolerance model replicates the tolerances used in design and machining process and encodes the distance of machined-machined (or sometimes machined-rough) features as axis-aligned minimum and maximum distance of feature points.
+These feature points can be a point of a plane or the center point of the end face of a cylinder for example.
+The tolerance evaluation is part of the objective optimization model which means that the distance of these features needs to be often calculated.
+%The distance of these features points, thus the evaluation of the tolerance depends on the position of these features which means that the tolerance values need to be evaluated while solving the optimization model.
+
+Evaluating the minimum machining allowance contributes to the constraints of the optimization program and depends on geometric calculations as well.
+The allowance calculation requires the position of the features as well as other geometric parameter (radii of cylinders for example).
+%TODO: még egy mondat?
+
+Objective of the optimization program is to achieve as little tolerance deviation as possible, while ensuring that material is removed for proper surface finish.
+These objectives and constraints are encoded into a convex quadratically constrained quadratic program (convex QCQP).
+While an appropriate solver is needed for this family of problems, the solver also needs to evaluate the above described tolerance model and geometric queries during solution.
+We detail this interaction in the next section, while the algorithm itself is described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}.
 
@@
 
-During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner as well.
+During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner.
 These needs include:

### 2025-04-04 paper/paper.tex
wip commit for the weekend

@@
 \input{header}
+%TODO: ha kell hely, akkor Jóska BME-t törölhetjük
 
@@
 It aims to precisely establish the geometric relation of the machine tool (mill, lathe, etc.) and the workpiece.
-We introduced the concept of multi-operation blank localization to address this task for drilling and milling scenarios in a semi-automated way, which allows positioning different machining features (e.g., different holes) separately in order to exploit the tolerances on the relative position of those features to compensate the small errors of the blank.
+We introduced the concept of multi-operation blank localization to address this task for drilling and milling scenarios in a semi-automated way,
+%TODO: innentől a mondat második fele cut?
+which allows positioning different machining features (e.g., different holes) separately in order to exploit the tolerances on the relative position of those features to compensate the small errors of the blank.
 The method takes as input the measured rough geometry and the machining CNC code, and computes the best possible position of each feature considering machining allowances and tolerances by solving a convex quadratically constrained quadratic program (QCQP).
@@
 Current practice is dominated by iterative adjustments by the human operator, which requires highly trained workers, takes a long time, and still, may produce scrap.
-Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object (\cite{ding:2021_CoarsefineOptimizationMethod}\cite{tan:2014_UnconstrainedApproachBlank}).
-Multi-operation blank localization was introduced in~\cite{cserteg:2023_Annals} focusing on drilling and milling.
-These machining operations are among the most used ones, therefore the method is applicable for a wide range of products.
-The abstract method and its implementation was developed in parallel, which required a language with support for easy prototyping and wide variety of tools.
+%TODO: kell egyáltalán ezeket hivatkozni?
+Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object \cite{ding:2021_CoarsefineOptimizationMethod}\cite{tan:2014_UnconstrainedApproachBlank}.
+Multi-operation blank localization~\cite{cserteg:2023_Annals} however handles group of features independently providing greater flexibility than traditional approaches.
+It focuses on drilling and milling which are among the most common machining operations, making it applicable to a wide range of products.
+The abstract method and its implementation were developed in parallel, which required a language with support for easy prototyping and wide variety of tools.
 Exactly for these reasons we chose the Julia language~\cite{bezanson2017julia}.
@@
 
-The algorithm looks for the optimal position for each feature group on the workpiece.
-Features within a group can be, for example, drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
-Features within the same group move together, but different feature groups can be moved separately.
-The to-be-machined features (short: machined features) need to "enclose" the features on the blank (called rough features) with a minimum machining allowance which ensures the required surface finish.
-While doing so, the dimensional tolerances between some features need to be respected, as these describe functional properties (e.g. connections to other mating parts).
+The problem involves looking for the optimal position for each to-be-machined feature (short: machined feature) on the workpiece.
+Based on the actual machining operations, these features are grouped into feature groups, for example, drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
+Features within the same group move together, but different feature groups can move separately.
+The machined features need to "enclose" the pre-cast features on the blank (called rough features) with a minimum machining allowance which ensures the required surface finish.
+While doing so, the dimensional tolerances between some features need to be respected, as these describe functional properties (e.g. connections to mating parts).
 Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals} shows an example of these features.
@@
 	\centerline{\includegraphics[width=0.95\columnwidth]{cirp-annals-2023-figure-2.png}}
-	\caption{3D scanned rough features (in grey), two machined feature groups with their part zeros (orange and purple), and tolerances that connect some features \cite{cserteg:2023_Annals}.}
+	\caption{3D scanned rough features (in grey), two machined feature groups (orange and purple) with their part zeros, and tolerances connecting features \cite{cserteg:2023_Annals}.}
 	%\caption{Measured part with two machined feature groups and tolerances between them.
@@
 
+Following common machining practice the objective of the optimization program is to achieve as little tolerance deviation as possible, while ensuring that material is removed for proper surface finish.
+The features are moved through their part zeros, which are the variables of the developed convex quadratically constrained quadratic program (convex QCQP).
+
+A tolerance model was developed to replicate the tolerances used in design and machining process.
+This model encodes the distance of machined-machined (or sometimes machined-rough) features as axis-aligned minimum and maximum distance.
+These distances form constraints in the optimization program, while minimizing the deviation relative to their mean (central?) value across all tolerances is the objective function itself.
+
+The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
+From these input data the rough-machined feature geometry pairs need to be extracted so that their machining allowance can be computed.
+The geometric parameters are extracted so the constraint equations for the minimum machining allowance can be generated for the optimization program.
+
+The optimization model itself and use-cases are described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}, while implementation details are given in the following section.
+
+%These feature points can be a point of a plane or the center point of the end face of a cylinder for example.
 %The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of removed material.
@@
 %Those two are bundled in a convex optimization problem.
-The developed tolerance model replicates the tolerances used in design and machining process and encodes the distance of machined-machined (or sometimes machined-rough) features as axis-aligned minimum and maximum distance of feature points.
-These feature points can be a point of a plane or the center point of the end face of a cylinder for example.
-The tolerance evaluation is part of the objective optimization model which means that the distance of these features needs to be often calculated.
+
+%TODO: kihagyni a feature pontokat egy az egyben: Distance of freatures
+%mi a feladat és milyen követelményeket támaszt az implementáció felé
+% előbb feladatról beszélni és utána julia implementáció követeleményekről?
+%todo: deklaratív megoldás
+% feladat specifikáció: rough leírás, megmunkálandó leírás, toleranciák (alkatrészrajz, cnc kód)
+% ebből a sokféle adatból készül a modell
+%modellépítés: összes korlátot és célfv-t definiálni kell és annak az összes paraméterét ki kell számolni
+% a geometriai számítűsok ahhoz kellenek, hogy kigeneráljuk a modell egyenleteit, amiknek önmagukban nincs jelentésük, mert csak egyenlőtlenségek.
+%megoldás: darál a solver. Nem csinálunk semmit. - tök általános célú QCQP solver, aminek az eredményét valahogy implementálni kell
+% kimenteni a part zerokat, és kiértékelni, hogy tolerancia ígyúgy, allownace ezaz meg vizualizáció
+
+%todo az absztrakt modellépítést implementálja a julia implementáció sokkal részletesebben
+% modellépítés és instancia generálás
+% modellépítés, mint adatokkal való feltöltés <- ezt a julia csinálja
+%The tolerance evaluation is part of the objective of the optimization model which means that the distance of these features needs to be often calculated.
 %The distance of these features points, thus the evaluation of the tolerance depends on the position of these features which means that the tolerance values need to be evaluated while solving the optimization model.
 
-Evaluating the minimum machining allowance contributes to the constraints of the optimization program and depends on geometric calculations as well.
-The allowance calculation requires the position of the features as well as other geometric parameter (radii of cylinders for example).
+%Evaluating the minimum machining allowance contributes to the constraints of the optimization program and depends on geometric calculations as well.
+%The allowance calculation requires the position of the features as well as other geometric parameter (radii of cylinders for example).
 %TODO: még egy mondat?
 
-Objective of the optimization program is to achieve as little tolerance deviation as possible, while ensuring that material is removed for proper surface finish.
-These objectives and constraints are encoded into a convex quadratically constrained quadratic program (convex QCQP).
-While an appropriate solver is needed for this family of problems, the solver also needs to evaluate the above described tolerance model and geometric queries during solution.
-We detail this interaction in the next section, while the algorithm itself is described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}.
+%While an appropriate solver is needed for this family of problems, the solver also needs to evaluate the above described tolerance model and geometric queries during solution.
+%We detail this interaction in the next section, while the algorithm itself is described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}.
 
@@
 
-During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner.
-These needs include:
+During the development of the algorithm, we needed a software tool that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner.
+We needed a tool that:
 
 \begin{itemize}
-	\item A versatile type system for geometrical representation, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
-	\item Easy-to-use interface for the optimization model.
-	\item Support for importing geometries from a variety of measurement tools (CMM, laser scanner, measurement arm).
-	\item Support for debugging, analyzing and visualizing the results.
+	\item Interfaces our model to the optimization solver and enables rapid prototyping.
+	\item Supports a variety of geometrical representations, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
+	\item Supports importing geometries from a variety of measurement tools (CMM, 3D scanner, measurement arm).
+%	\item Supports easy extension of the geometries if required.
+%	\item Supports extending 
+%	\item Translates the tolerance model for the optimization solver.
+	\item Supports easy debugging and helps analyzing and visualizing the results.
 \end{itemize}
 
-A flexible type system is designed to handle the different representations of geometries and features.
-Abstract hole and plane geometries model the drilling and milling operations, while traits describe if a feature uses a free-form or a primitive representation.
-An internal API (set of functions) is designed to access the relevant properties of the geometries (center point, radius, surface points, etc.).
+The heart of the implementation is the solver provided by the JuMP ecosystem~\cite{Lubin2023}.
+With JuMP's excellent design, implementing the optimization model was as easy as repeating the mathematical model in Julia.
+Other advantage of the JuMP ecosystem is that solvers can be easily swapped if needed.
+For development, the FICO Xpress solver was used, but our industry partner could use the Ipopt or SCIP solvers without issue.
 
-This internal API is used when constructing the optimization model utilizing the JuMP ecosystem~\cite{Lubin2023}.
-With JuMP's excellent design, coding the optimization model was as easy as repeating the mathematical model in Julia.
-Other advantage of the JuMP ecosystem is that solvers can be easily swapped if needed.
-For development, the FICO Xpress solver was used (with academic license), but our industry partner could use the Ipopt or SCIP solvers without issue.
-Using the internal API gives the advantage that new geometry representations can be quickly used with the optimization model by just implementing a new type and a set of functions.
+%TODO: azt kell elmagyarázni, hogy különböző geometria reprezentációk vannak különböző mérésekből
+% de nekünk mindig ugyanaz az információ: a feature point kell
+% és ezzel az interfésszel mindenféle mérőeszköz formátumát le tudjuk kezelni
+% és van egy egységes interface a feautre pointok (geometriaia leírók, paraméterek?) lekérdezéséhez
+
+To generate the optimization model we needed to store the 1. nc code 2. rough geometry 3. tolerances.
+A common thing regarding the first two, that some kind of geometric representation is needed.
+Representing the NC code can be done with plane and cylinder geometries for milling and drilling operations.
+While the rough geometry poses greater challanges.
+Different measurements instruments output different type of geometric data, for example a coordinate measurement arm (CMM) will provide primitive geometry definitions like disks and cylinders while a 3D scanner output point clouds or meshes (pongyolán csak free form).
+Property of the optimization model is that it is built around "feature points" (consistently defined points of different geometries).
+These two aspects required us to develop a type tree.
+To cover our current needs (drilling and milling operations), planar and cylindrical geometries are defined.
+The other property of geometries is if they are primitive or free form, which is covered by the holy trait pattern.
+\texttt{IsPrimitve} or \texttt{IsFreeForm} traits can be applied to geometry types independently of their planar or cylindrical type.
+Code block~\ref{lst:def-types} shows the core of the implementation of the type system.
+
+\begin{lstlisting}[language = Julia, numbers=left, label={lst:def-types}, caption={Draft of the type system used by \texttt{BlankLocalizationCore.jl}.}]
+# Supertype for localization geometries.
+# "A": abbr. for Abstract
+# "L": abbr. for Localization
+abstract type ALocGeometry end
+abstract type AHoleGeometry <: ALocGeometry end
+abstract type APlaneGeometry <: ALocGeometry end
+
+# Trait to describe the "style" of an ALocGeometry.
+abstract type GeometryStyle end
+struct IsPrimitive <: GeometryStyle end
+struct IsFreeForm <: GeometryStyle end
+\end{lstlisting}
+
+The other part of the optimization generation interface is definition of the query functions that work on these types.
+Free form geometries need to implement the \texttt{surfacepoints} and \texttt{filteredsurfacepoints} methods;
+Primitive geometries need to have the \texttt{featurepoint} method and cylindrical features need the \texttt{featureradius} on top of that.
+For visualization the \texttt{visualizationgeometry} function need to be defined whose output is passed to \texttt{Meshes.viz} function, so Meshes objects are needed.
+A short example for such a definition is shown in code block~\ref{lst:example}.
+
+The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
+Using the Meshes ecosystem, we could produce publication quality images, like Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals}.
+
+\begin{lstlisting}[language = Julia, numbers=left, label={lst:example}, caption={Defining a new type.}]
+struct MyDisk <: AHoleGeometry
+  p::Vector{Float64} # center point
+  n::Vector{Float64} # surface normal
+  d::Float64 # diameter
+end
+GeometryStyle(::Type{MyDisk}) = IsPrimitive()
+
+featurepoint(::IsPrimitive, x::MyDisk) = x.p
+featureradius(::IsPrimitive, x::MyDisk) = x.d/2
+
+using Meshes
+
+function visualizationgeometry(geom::MyDisk)
+  plane = Plane(Point3(geom.p), Vec3(geom.n))
+  return Disk(plane, geom.d/2)
+end
+\end{lstlisting}
+
+The optimization program uses a feature point (or feature points for free form geometries) of features, that is used for computing the machining allowance and the dimensional tolerances.
+A function interface is defined for querying these feature points of geometries, that is used to generate the optimization program.
+Code block~\ref{lst:example} shows the definition of those functions as well.
+The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
+Using the Meshes ecosystem, we could produce publication quality images, like Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals}.
+
+The optimization generation engine uses the functions defined by this interface to construct the optimization program.
 
@@
 
-The geometric computations are implemented with the help of the \texttt{Meshes.jl} package, which enabled us to easily visualize the geometries and results from the beginnings, see Fig.~\ref{fig:hatfig} for an example.
-
 \section{Results and future work}
 \label{sec:results}
-
-Fig.~\ref{fig:pareto} shows the allowance-tolerance pairs for an experiment from \cite{cserteg:2023_Annals}.
-The diagram illustrates that the proposed algorithm (blue curve) leads to lower tolerance errors for any given machining allowance than earlier approaches, and it can also ensure significantly larger machining allowance.
-Obviously, there is a trade-off between small tolerance error and large machining allowance.
-Preliminary results were first published in \cite{cserteg:2023_DigitalTwinAssisted}.
-A journal paper describes the original algorithm \cite{cserteg:2023_Annals}, and a conference paper details the modifications for free-form surfaces \cite{cserteg:2023_CMS}.
-
-\begin{figure}[t]
-	\centerline{\includegraphics[width=0.95\columnwidth]{pareto-new-label.png}}
-	\caption{Balancing the machining allowance and the tolerance error \cite{cserteg:2023_Annals}.}
-	\label{fig:pareto}
-\end{figure}
-
+%TODO
 Future plans for the package and the method itself include an overhaul of the tolerance modeling scheme.

### 2025-04-10 paper/paper.tex
pushing updates preparing for final review

@@
 Cast parts may have small geometric variations from lot to lot that need to be addressed before machining by altering the CNC code.
-Current practice is dominated by iterative adjustments by the human operator, which requires highly trained workers, takes a long time, and still, may produce scrap.
+Current practice is dominated by iterative adjustments by human operators, which requires highly trained workers and takes a long time.
+%, and still, may produce scrap.
 %TODO: kell egyáltalán ezeket hivatkozni?
@@
 It focuses on drilling and milling which are among the most common machining operations, making it applicable to a wide range of products.
-The abstract method and its implementation were developed in parallel, which required a language with support for easy prototyping and wide variety of tools.
+The abstract method and its implementation were developed in parallel, which required a language with wide variety of tools and support for easy prototyping.
 Exactly for these reasons we chose the Julia language~\cite{bezanson2017julia}.
@@
 The problem involves looking for the optimal position for each to-be-machined feature (short: machined feature) on the workpiece.
-Based on the actual machining operations, these features are grouped into feature groups, for example, drilled holes on the same side of the part, whose drilling positions are defined relative to a common reference (the part zero).
-Features within the same group move together, but different feature groups can move separately.
+%chatgpt
+These features are grouped together, with each group defined relative to a specific reference point known as the part zero.
+The layout of these part zeros is controlled by the structure of the machining CNC code.
+By moving the part zeros, we can indirectly control the positions of the associated features.
+Each part zero—and by extension, each group—can be moved independently, which gives the method its flexibility.
+In the optimization program, the positions of the part zeros are the decision variables.
+
+%eredeti
+\iffalse
+These features are structured into groups, each group being defined relative to a common reference, called part zero.
+This is defined by the structure of the machining CNC code.
+This means that we can influence the features' positions through moving the part zeros.
+Part zeros (thus the groups) can be moved separately, which gives the method its flexibility.
+The position of the part zeros are the decision variables of the optimization program.
+\fi
+%Features within the same group must be moved together, but different feature groups can be moved separately.
+%TODO: optimalizáló leírás:
+% 0. motiváció
+% 1. mik a döntések
+% 2. mik a korlátok
+% 3. mi a célfv
+
 The machined features need to "enclose" the pre-cast features on the blank (called rough features) with a minimum machining allowance which ensures the required surface finish.
-While doing so, the dimensional tolerances between some features need to be respected, as these describe functional properties (e.g. connections to mating parts).
-Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals} shows an example of these features.
+The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
+From their positions and geometric parameters their distance can be computed, which then can be used to generate the allowance constraints for the optimization program.
 
-\begin{figure}[hbt]
+The other set of constraints roots from respecting the dimensional tolerances describing functional properties (e.g. connections to mating parts).
+The developed tolerance model encodes the distance of machined-machined (or sometimes machined-rough) features as axis-aligned minimum and maximum distance.
+%These distances form constraints in the optimization program, while minimizing the deviation relative to their mean (central?) value across all tolerances is the objective function itself.
+Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals} shows some examples for these features.
+
+\begin{figure}[b]
 	\centerline{\includegraphics[width=0.95\columnwidth]{cirp-annals-2023-figure-2.png}}
-	\caption{3D scanned rough features (in grey), two machined feature groups (orange and purple) with their part zeros, and tolerances connecting features \cite{cserteg:2023_Annals}.}
+	\caption{3D scanned rough features (in grey), two machined feature groups (orange and purple) with their part zeros, and tolerances connecting the machined features~\cite{cserteg:2023_Annals}.}
 	%\caption{Measured part with two machined feature groups and tolerances between them.
@@
 
-Following common machining practice the objective of the optimization program is to achieve as little tolerance deviation as possible, while ensuring that material is removed for proper surface finish.
-The features are moved through their part zeros, which are the variables of the developed convex quadratically constrained quadratic program (convex QCQP).
+%A tolerance model was developed to replicate the tolerances used in design and machining process.
 
-A tolerance model was developed to replicate the tolerances used in design and machining process.
-This model encodes the distance of machined-machined (or sometimes machined-rough) features as axis-aligned minimum and maximum distance.
-These distances form constraints in the optimization program, while minimizing the deviation relative to their mean (central?) value across all tolerances is the objective function itself.
-
-The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
-From these input data the rough-machined feature geometry pairs need to be extracted so that their machining allowance can be computed.
-The geometric parameters are extracted so the constraint equations for the minimum machining allowance can be generated for the optimization program.
-
+% vagy full stop, vagy "while ensuring the above constraints are respected
+Following common machining practice, the objective of the optimization program is to achieve as little tolerance deviation as possible.
+The problem is formulated as a convex quadratically constrained quadratic program (convex QCQP).
+%, where decision variables are the positions of the part zeros.
+%TODO az hogy a part zeroval mozgatunk, az legyen tisztázva korábban
+%The features are moved through their part zeros, which are the variables of the developed .
 The optimization model itself and use-cases are described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}, while implementation details are given in the following section.
@@
 %The allowance calculation requires the position of the features as well as other geometric parameter (radii of cylinders for example).
-%TODO: még egy mondat?
 
@@
 
-During the development of the algorithm, we needed a software tool that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner.
-We needed a tool that:
+%The following aspects of julia enabled us to develop the model and its implementation quickly and efficiently
+%During the development of the algorithm, the following requirements were formulated::
+%we needed a software tool that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner.
+%Summarizin
+%Julia helped us to develop the implementation that had the following properties
 
+%The implementation needed to be ilyen, which 
+Julia enabled us to develop an implementation with the following properties:
 \begin{itemize}
-	\item Interfaces our model to the optimization solver and enables rapid prototyping.
-	\item Supports a variety of geometrical representations, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
-	\item Supports importing geometries from a variety of measurement tools (CMM, 3D scanner, measurement arm).
-%	\item Supports easy extension of the geometries if required.
-%	\item Supports extending 
-%	\item Translates the tolerance model for the optimization solver.
-	\item Supports easy debugging and helps analyzing and visualizing the results.
+	%TODO: vagy legyen két rész a rapid prototypinggal vagy skip
+	\item Concise interface to generate the parameters of the declarative optimization program based on procedural geometric calculations.
+%	\item Interfaces our model to the optimization solver and enables rapid prototyping.
+	\item Support for a variety of geometrical representations, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representations.
+	\item Support for analyzing and visualizing the results.
 \end{itemize}
 
+%TODO: asbtract type system is a good base for handling the import fnctions for the measuremnt tool
+
 The heart of the implementation is the solver provided by the JuMP ecosystem~\cite{Lubin2023}.
-With JuMP's excellent design, implementing the optimization model was as easy as repeating the mathematical model in Julia.
-Other advantage of the JuMP ecosystem is that solvers can be easily swapped if needed.
-For development, the FICO Xpress solver was used, but our industry partner could use the Ipopt or SCIP solvers without issue.
+With JuMP's excellent design, combining the necessary geometric calculations and the declarative optimization program definition was straightforward.
+%implementing the optimization model was as easy as repeating the mathematical model in Julia.
+%TODO
+%jjumps support for declarative programming meets with julia's abstract type system and procedural techniques for geometrical computations
+% az együtthatókat könnyű volt juliaból generálni, mert absztrakt módon könnyű megkeresni őket (vagy mi)
+Other advantage of JuMP is that solvers can be easily swapped.
+For development, the (commercial) FICO Xpress solver was used, but our industry partner could use the (open source) Ipopt or SCIP solvers without issue.
+
+%TODO: absztrakt typusokra deinfinájuk a funckiókat, amiket aztán alacsony sznten könnyű implementálni
 
@@
 
-To generate the optimization model we needed to store the 1. nc code 2. rough geometry 3. tolerances.
-A common thing regarding the first two, that some kind of geometric representation is needed.
-Representing the NC code can be done with plane and cylinder geometries for milling and drilling operations.
-While the rough geometry poses greater challanges.
-Different measurements instruments output different type of geometric data, for example a coordinate measurement arm (CMM) will provide primitive geometry definitions like disks and cylinders while a 3D scanner output point clouds or meshes (pongyolán csak free form).
-Property of the optimization model is that it is built around "feature points" (consistently defined points of different geometries).
-These two aspects required us to develop a type tree.
-To cover our current needs (drilling and milling operations), planar and cylindrical geometries are defined.
-The other property of geometries is if they are primitive or free form, which is covered by the holy trait pattern.
-\texttt{IsPrimitve} or \texttt{IsFreeForm} traits can be applied to geometry types independently of their planar or cylindrical type.
-Code block~\ref{lst:def-types} shows the core of the implementation of the type system.
+To handle the tolerance and allowance calculations, the part definition (CNC code), rough geometry measurements and tolerances need to be stored.
+Their representation is built upon a flexible geometry type system.
+%To generate the optimization model we needed to store the 1. nc code 2. rough geometry 3. tolerances.
+%A common thing regarding the first two, that some kind of geometric representation is needed.
 
-\begin{lstlisting}[language = Julia, numbers=left, label={lst:def-types}, caption={Draft of the type system used by \texttt{BlankLocalizationCore.jl}.}]
-# Supertype for localization geometries.
-# "A": abbr. for Abstract
-# "L": abbr. for Localization
+The CNC code can be represented with plane and cylinder geometries for milling and drilling operations.
+This "type" information of the geometries is encoded with Julia types.
+The primitive or free-form nature of the geometries is implemented with the holy traits pattern and is necessary because different instruments output different types of geometric data.
+For example, a coordinate measurement machine will provide primitive geometry definitions like disks and cylinders, while a 3D scanner outputs point clouds or meshes (called free-form collectively).
+The \texttt{IsPrimitve} or \texttt{IsFreeForm} traits are applied to geometry types independently of their planar or cylindrical type.
+Code block~\ref{lst:def-types} shows a shortened version of the implemented type system.
+
+\begin{lstlisting}[language = Julia, numbers=left, label={lst:def-types}, caption={Shortened implementation of the type system used by \texttt{BlankLocalizationCore.jl}.}]
+# Type tree for localization geometries.
+# "ALoc": AbstractLocalization
 abstract type ALocGeometry end
@@
 
-The other part of the optimization generation interface is definition of the query functions that work on these types.
-Free form geometries need to implement the \texttt{surfacepoints} and \texttt{filteredsurfacepoints} methods;
-Primitive geometries need to have the \texttt{featurepoint} method and cylindrical features need the \texttt{featureradius} on top of that.
-For visualization the \texttt{visualizationgeometry} function need to be defined whose output is passed to \texttt{Meshes.viz} function, so Meshes objects are needed.
-A short example for such a definition is shown in code block~\ref{lst:example}.
+The optimization model uses a "feature point" concept which requires the position and some parameters of the geometries.
+A function interface is designed for accessing these values.
+%is that it is built around "feature points" (consistently defined points of different geometries).
+%The other part of the optimization generation interface is definition of the query functions that work on these types.
+The package documentation contains the list of functions that need to be defined but some are showcased in code block~\ref{lst:example}.
+%Free form geometries need to implement the \texttt{surfacepoints} and \texttt{filteredsurfacepoints} methods;
+%Primitive geometries need to have the \texttt{featurepoint} method and cylindrical features need the \texttt{featureradius} on top of that.
+One function that we want to highlight is the \texttt{visualizationgeometry}, which needs to return a \texttt{Meshes.jl} object that will be passed to the \texttt{Meshes.viz} function.
+%The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
+Using the Meshes ecosystem~\cite{Hoffimann2023}, we could not only interactively inspect the results of the optimization, but also produce publication quality images, like Fig.~\ref{fig:hatfig} in \cite{cserteg:2023_Annals}.
 
-The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
-Using the Meshes ecosystem, we could produce publication quality images, like Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals}.
+\vspace*{2em}
 
-\begin{lstlisting}[language = Julia, numbers=left, label={lst:example}, caption={Defining a new type.}]
+\begin{lstlisting}[language = Julia, numbers=left, label={lst:example}, caption={Defining a new type for the optimization model.}]
 struct MyDisk <: AHoleGeometry
@@
 end
+
 GeometryStyle(::Type{MyDisk}) = IsPrimitive()
@@
 
-The optimization program uses a feature point (or feature points for free form geometries) of features, that is used for computing the machining allowance and the dimensional tolerances.
+\iffalse
+The optimization program uses a feature point (or feature points for free-form geometries) of features, that is used for computing the machining allowance and the dimensional tolerances.
 A function interface is defined for querying these feature points of geometries, that is used to generate the optimization program.
@@
 As a result, we needed to write (or use) parsers for different text and tabular formats.
+\fi
 

### 2025-04-10 paper/paper.tex
finalize paper

@@
 %TODO: kell egyáltalán ezeket hivatkozni?
-Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object \cite{ding:2021_CoarsefineOptimizationMethod}\cite{tan:2014_UnconstrainedApproachBlank}.
-Multi-operation blank localization~\cite{cserteg:2023_Annals} however handles group of features independently providing greater flexibility than traditional approaches.
+Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object \cite{tan:2014_UnconstrainedApproachBlank}.
+Multi-operation blank localization~\cite{cserteg:2023_Annals} however handles groups of features independently, providing greater flexibility than traditional approaches.
 It focuses on drilling and milling which are among the most common machining operations, making it applicable to a wide range of products.
@@
 
-The machined features need to "enclose" the pre-cast features on the blank (called rough features) with a minimum machining allowance which ensures the required surface finish.
+To ensure the required surface finish, the machined features must enclose the pre-cast features on the blank (called rough features) with a minimum machining allowance (a lower bound parameter).
 The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
@@
 %TODO: asbtract type system is a good base for handling the import fnctions for the measuremnt tool
-
-The heart of the implementation is the solver provided by the JuMP ecosystem~\cite{Lubin2023}.
+The implementation is built around JuMP~\cite{Lubin2023}, which serves as the interface to the underlying optimization solver.
 With JuMP's excellent design, combining the necessary geometric calculations and the declarative optimization program definition was straightforward.
@@
 %The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
-Using the Meshes ecosystem~\cite{Hoffimann2023}, we could not only interactively inspect the results of the optimization, but also produce publication quality images, like Fig.~\ref{fig:hatfig} in \cite{cserteg:2023_Annals}.
+Using the Meshes ecosystem~\cite{Hoffimann2023}, we could not only interactively inspect the results of the optimization, but also produce publication quality images, like Fig.~\ref{fig:hatfig}.
 
-\vspace*{2em}
+\vspace*{1em}
 

### 2025-04-10 paper/paper.tex
remove comments and old text chunks from paper

@@
 \input{header}
-%TODO: ha kell hely, akkor Jóska BME-t törölhetjük
 
@@
 We introduced the concept of multi-operation blank localization to address this task for drilling and milling scenarios in a semi-automated way,
-%TODO: innentől a mondat második fele cut?
 which allows positioning different machining features (e.g., different holes) separately in order to exploit the tolerances on the relative position of those features to compensate the small errors of the blank.
@@
 Current practice is dominated by iterative adjustments by human operators, which requires highly trained workers and takes a long time.
-%, and still, may produce scrap.
-%TODO: kell egyáltalán ezeket hivatkozni?
 Automated methods exist for complex free-form parts like wind turbines that place the entire blank as a single solid object \cite{tan:2014_UnconstrainedApproachBlank}.
@@
 The problem involves looking for the optimal position for each to-be-machined feature (short: machined feature) on the workpiece.
-%chatgpt
 These features are grouped together, with each group defined relative to a specific reference point known as the part zero.
@@
 In the optimization program, the positions of the part zeros are the decision variables.
-
-%eredeti
-\iffalse
-These features are structured into groups, each group being defined relative to a common reference, called part zero.
-This is defined by the structure of the machining CNC code.
-This means that we can influence the features' positions through moving the part zeros.
-Part zeros (thus the groups) can be moved separately, which gives the method its flexibility.
-The position of the part zeros are the decision variables of the optimization program.
-\fi
-%Features within the same group must be moved together, but different feature groups can be moved separately.
-%TODO: optimalizáló leírás:
-% 0. motiváció
-% 1. mik a döntések
-% 2. mik a korlátok
-% 3. mi a célfv
 
@@
 The developed tolerance model encodes the distance of machined-machined (or sometimes machined-rough) features as axis-aligned minimum and maximum distance.
-%These distances form constraints in the optimization program, while minimizing the deviation relative to their mean (central?) value across all tolerances is the objective function itself.
 Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals} shows some examples for these features.
@@
 	\caption{3D scanned rough features (in grey), two machined feature groups (orange and purple) with their part zeros, and tolerances connecting the machined features~\cite{cserteg:2023_Annals}.}
-	%\caption{Measured part with two machined feature groups and tolerances between them.
-$r^M$ and $r^R$ denote the machined and rough radii of a feature, while $\delta$ the machining allowance \cite{cserteg:2023_Annals}.}
 	\label{fig:hatfig}
@@
 
-%A tolerance model was developed to replicate the tolerances used in design and machining process.
-
-% vagy full stop, vagy "while ensuring the above constraints are respected
 Following common machining practice, the objective of the optimization program is to achieve as little tolerance deviation as possible.
 The problem is formulated as a convex quadratically constrained quadratic program (convex QCQP).
-%, where decision variables are the positions of the part zeros.
-%TODO az hogy a part zeroval mozgatunk, az legyen tisztázva korábban
-%The features are moved through their part zeros, which are the variables of the developed .
 The optimization model itself and use-cases are described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}, while implementation details are given in the following section.
-
-%These feature points can be a point of a plane or the center point of the end face of a cylinder for example.
-%The former encodes the requirement that material needs to be removed to ensure proper surface finish and is described for a feature as the smallest thickness of removed material.
-%A dimensional tolerance between two features is modeled as lower and upper bounds on the distance between the two features.
-%As feature groups move together, only inter-group tolerances need to be considered.
-
-%Briefly we can summarize the multi-operation blank localization as a method that aligns the machined and rough geometries with the required minimum overlap.
-%It does it while making sure that features that are connected by dimensional tolerances are within the required distance range.
-
-%Tolerance model is used
-%Geometric computations
-%Those two are bundled in a convex optimization problem.
-
-%TODO: kihagyni a feature pontokat egy az egyben: Distance of freatures
-%mi a feladat és milyen követelményeket támaszt az implementáció felé
-% előbb feladatról beszélni és utána julia implementáció követeleményekről?
-%todo: deklaratív megoldás
-% feladat specifikáció: rough leírás, megmunkálandó leírás, toleranciák (alkatrészrajz, cnc kód)
-% ebből a sokféle adatból készül a modell
-%modellépítés: összes korlátot és célfv-t definiálni kell és annak az összes paraméterét ki kell számolni
-% a geometriai számítűsok ahhoz kellenek, hogy kigeneráljuk a modell egyenleteit, amiknek önmagukban nincs jelentésük, mert csak egyenlőtlenségek.
-%megoldás: darál a solver. Nem csinálunk semmit. - tök általános célú QCQP solver, aminek az eredményét valahogy implementálni kell
-% kimenteni a part zerokat, és kiértékelni, hogy tolerancia ígyúgy, allownace ezaz meg vizualizáció
-
-%todo az absztrakt modellépítést implementálja a julia implementáció sokkal részletesebben
-% modellépítés és instancia generálás
-% modellépítés, mint adatokkal való feltöltés <- ezt a julia csinálja
-%The tolerance evaluation is part of the objective of the optimization model which means that the distance of these features needs to be often calculated.
-%The distance of these features points, thus the evaluation of the tolerance depends on the position of these features which means that the tolerance values need to be evaluated while solving the optimization model.
-
-%Evaluating the minimum machining allowance contributes to the constraints of the optimization program and depends on geometric calculations as well.
-%The allowance calculation requires the position of the features as well as other geometric parameter (radii of cylinders for example).
-
-%While an appropriate solver is needed for this family of problems, the solver also needs to evaluate the above described tolerance model and geometric queries during solution.
-%We detail this interaction in the next section, while the algorithm itself is described in \cite{cserteg:2023_CMS} and \cite{cserteg:2023_Annals}.
 
@@
 
-%The following aspects of julia enabled us to develop the model and its implementation quickly and efficiently
-%During the development of the algorithm, the following requirements were formulated::
-%we needed a software tool that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner.
-%Summarizin
-%Julia helped us to develop the implementation that had the following properties
-
-%The implementation needed to be ilyen, which 
 Julia enabled us to develop an implementation with the following properties:
 \begin{itemize}
-	%TODO: vagy legyen két rész a rapid prototypinggal vagy skip
 	\item Concise interface to generate the parameters of the declarative optimization program based on procedural geometric calculations.
-%	\item Interfaces our model to the optimization solver and enables rapid prototyping.
 	\item Support for a variety of geometrical representations, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representations.
@@
 
-%TODO: asbtract type system is a good base for handling the import fnctions for the measuremnt tool
 The implementation is built around JuMP~\cite{Lubin2023}, which serves as the interface to the underlying optimization solver.
 With JuMP's excellent design, combining the necessary geometric calculations and the declarative optimization program definition was straightforward.
-%implementing the optimization model was as easy as repeating the mathematical model in Julia.
-%TODO
-%jjumps support for declarative programming meets with julia's abstract type system and procedural techniques for geometrical computations
-% az együtthatókat könnyű volt juliaból generálni, mert absztrakt módon könnyű megkeresni őket (vagy mi)
 Other advantage of JuMP is that solvers can be easily swapped.
@@
 
-%TODO: absztrakt typusokra deinfinájuk a funckiókat, amiket aztán alacsony sznten könnyű implementálni
-
-%TODO: azt kell elmagyarázni, hogy különböző geometria reprezentációk vannak különböző mérésekből
-% de nekünk mindig ugyanaz az információ: a feature point kell
-% és ezzel az interfésszel mindenféle mérőeszköz formátumát le tudjuk kezelni
-% és van egy egységes interface a feautre pointok (geometriaia leírók, paraméterek?) lekérdezéséhez
-
 To handle the tolerance and allowance calculations, the part definition (CNC code), rough geometry measurements and tolerances need to be stored.
 Their representation is built upon a flexible geometry type system.
-%To generate the optimization model we needed to store the 1. nc code 2. rough geometry 3. tolerances.
-%A common thing regarding the first two, that some kind of geometric representation is needed.
 
@@
 A function interface is designed for accessing these values.
-%is that it is built around "feature points" (consistently defined points of different geometries).
-%The other part of the optimization generation interface is definition of the query functions that work on these types.
 The package documentation contains the list of functions that need to be defined but some are showcased in code block~\ref{lst:example}.
-%Free form geometries need to implement the \texttt{surfacepoints} and \texttt{filteredsurfacepoints} methods;
-%Primitive geometries need to have the \texttt{featurepoint} method and cylindrical features need the \texttt{featureradius} on top of that.
 One function that we want to highlight is the \texttt{visualizationgeometry}, which needs to return a \texttt{Meshes.jl} object that will be passed to the \texttt{Meshes.viz} function.
-%The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
 Using the Meshes ecosystem~\cite{Hoffimann2023}, we could not only interactively inspect the results of the optimization, but also produce publication quality images, like Fig.~\ref{fig:hatfig}.
@@
 
-\iffalse
-The optimization program uses a feature point (or feature points for free-form geometries) of features, that is used for computing the machining allowance and the dimensional tolerances.
-A function interface is defined for querying these feature points of geometries, that is used to generate the optimization program.
-Code block~\ref{lst:example} shows the definition of those functions as well.
-The visulization interface is built around Meshes.jl, therefore the to-be-showed geometries must be from that package.
-Using the Meshes ecosystem, we could produce publication quality images, like Fig.~\ref{fig:hatfig} from \cite{cserteg:2023_Annals}.
-
-The optimization generation engine uses the functions defined by this interface to construct the optimization program.
-
-As mentioned earlier, an important requirement was to handle the output formats of many different devices.
-Every measurement instrument comes with its own processing software and export formats, not necessarily designed for interoperability.
-As a result, we needed to write (or use) parsers for different text and tabular formats.
-\fi
-
 \section{Results and future work}
 \label{sec:results}
-%TODO
+
 Future plans for the package and the method itself include an overhaul of the tolerance modeling scheme.

### 2025-04-10 paper/paper.tex
update future plans to match article updates

@@
 
-Future plans for the package and the method itself include an overhaul of the tolerance modeling scheme.
-Currently, only dimensional tolerances are handled, but it should be discovered if more GD\&T tolerances can be incorporated into the model.
-The current implementation supports only cylinders and planes, thus drilling and milling; it is a future research direction to extend the handled machining operations, e.g., to turning.
+Future plans for the package and the method itself include an overhaul of the tolerance modelling scheme.
+It should be possible to generalize the current dimensional tolerances for  more GD\&T tolerances by introducing a new type hierarchy based on the current geometry type tree and a function interface for the optimization program.
+Another direction of development is to extend the supported operations from drilling and milling to others, such as turning, although this is more a research question than an implementation.
 

### 2025-04-11 paper/paper.tex
final touches

@@
 
-To ensure the required surface finish, the machined features must enclose the pre-cast features on the blank (called rough features) with a minimum machining allowance (a lower bound parameter).
+To ensure the required surface finish, the machined features must enclose the pre-cast features (rough features) on the blank with a minimum machining allowance (a lower bound parameter).
 The allowance calculation requires the final part specification in the form of the machining CNC code as well as a representation of the rough geometries.
@@
 It should be possible to generalize the current dimensional tolerances for  more GD\&T tolerances by introducing a new type hierarchy based on the current geometry type tree and a function interface for the optimization program.
-Another direction of development is to extend the supported operations from drilling and milling to others, such as turning, although this is more a research question than an implementation.
+Another direction of development is to extend the supported operations from drilling and milling to others, such as turning, although this is more of a research question than an implementation issue.
 

### 2025-04-11 docs/make.jl
build documentation for PRs

@@ -25,4 +25,5 @@ makedocs(;
 deploydocs(;
     repo="github.com/cserteGT3/BlankLocalizationCore.jl",
     devbranch="main",
+    push_preview = true
 )

### 2025-04-11 previews/PR39/search_index.js
build based on 4e56865

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"api/#Using-the-API-to-extend-the-geometry-types","page":"API extension","title":"Using the API to extend the geometry types","text":"","category":"section"},{"location":"api/","page":"API extension","title":"API extension","text":"The solver handles hole and face (plane) features that are either IsPrimitive or IsFreeForm. A few basic types are defined like SimpleHole and MeshHole, but new ones can be also defined. For example for point clouds, that don't have faces, like a mesh, only points.","category":"page"},{"location":"api/","page":"API extension","title":"API extension","text":"This capability is properly documented, as a major API rewrite is going on in #3.","category":"page"},{"location":"api/#Defining-a-new-geometry","page":"API extension","title":"Defining a new geometry","text":"","category":"section"},{"location":"api/","page":"API extension","title":"API extension","text":"Defining a new geometry is pretty easy:","category":"page"},{"location":"api/","page":"API extension","title":"API extension","text":"It has to be the subtype of either AbstractHoleGeometry or AbstractPlaneGeometry.\nThe GeometryStyle trait is need to be defined: it is either a IsPrimitive or IsFreeForm geometry.\nIsFreeForm geometries need to define the surfacepoints and filteredsurfacepoints functions.\nIsPrimitive geometries need to define the featurepoint functions\nThose IsPrimitive geometries that are subtype of AbstractHoleGeometry also need to define the featureradius function\nFinally, for visualization purposes the visualizationgeometry function should be defined, that returns an object, that can be used with the Meshviz.viz() function.","category":"page"},{"location":"api/#An-example","page":"API extension","title":"An example","text":"","category":"section"},{"location":"api/","page":"API extension","title":"API extension","text":"Let's assume that we want to define a new holelike type: MyDisk, which has a featurepoint, a normal, and a radius.","category":"page"},{"location":"api/","page":"API extension","title":"API extension","text":"using BlankLocalizationCore\n\nstruct MyDisk <: AbstractHoleGeometry\n    point::Vector{Float64}\n    normal::Vector{Float64}\n    diameter::Float64\nend\n\nGeometryStyle(::Type{MyDisk}) = IsPrimit
[…]
